### 2016-02-05 gd358fit.tex
Still having issues with the journal table.  Forcing Latex to run does create the table.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{List of 15 Periods Used in GD358 Fit.  
\label{gd}
}
\tablehead{

\colhead{$k$} & \colhead{Frequency}& \colhead{Period} & \colhead{Uncertainty} & \colhead{Best fit periods}  \\
\colhead{(\muHz)}  & \colhead{(s)} & \colhead{(\muHz)} & \colhead{(s)} & \colhead{(s)} \\
}
\startdata

8  &2363.318 & 423.13 & 0.04 & 426.539 \\
9  &2155.544 & 463.92 & 0.04 & 465.282 \\
10 &2007.628 & 497.83 & 0.2 & 498.088 \\
11 &1857.716 & 538.30 & 0.3 & 541.349 \\
12 &1741.505 & 574.22 & 0.1 & 572.361 \\
13 &1619.700 & 617.40 & 0.2 & 615.581 \\
14 &1518.160 & 658.69 & 0.5 & 658.698 \\
15 &1428.943 & 699.82 & 0.2 & 701.322 \\
16 &1369.336 & 730.28 & 0.8 & 729.084 \\
17 &1299.147 & 769.74 & 0.2 & 770.469 \\
18 &1238.129 & 807.67 & 0.2 & 813.484 \\
19 &1170.207 & 854.55 & 0.6 & 851.921 \\
20 &1109.271 & 901.49 & 0.8 & 896.257 \\
22 &1032.967 & 968.09 & 1.4 & 960.588 \\
24 &941.333  & 1062.32 & 3.1 & 1056.794\\
\hline
 &  &  & & $\sigma_{\rm{rms}}$   & 3.12~s\\
\tableline
\enddata
\tablecaption{A list of the 15 periods used in the present fit of GD 358. We also include the corresponding periods 
from the best fit model (section ref{}). The $k$ identification is listed for each mode. There is strong evidence that 
all modes belong to an $\ell=1$ sequence. We assume that all the periods listed correspond to the $m=0$ 
component of any multiplet.\label{t1}}
\end{deluxetable}

### 2016-02-05 msnew.tex
Still having issues with the journal table.  Forcing Latex to run does create the table.

%\documentclass[manuscript,natbib]{aastex}
\documentclass[12pt,preprint]{aastex}

%%\newcommand{\vdag}{(v)^\dagger}
\newcommand{\bvf}{Brunt-V\"ais\"al\"a }
\newcommand{\teff}{$\rm T_{eff}$}
\newcommand{\logg}{$\log$g }
\newcommand{\kic}{kic}
\newcommand{\kicnsp}{kic }
\newcommand{\sigrms}{$\sigma_{\rm RMS}$}
\newcommand{\mstar}{$M_*$}
\newcommand{\menv}{$M_{\rm env}$}
\newcommand{\mhe}{$M_{\rm He}$}
\newcommand{\xo}{$X_o$}
\newcommand{\qfm}{$q_{\rm fm}$}
\newcommand{\muHz}{\mbox{$\mu$Hz}}
\newcommand{\msun}{$M_\odot$}

\shorttitle{Asteroseismology of GD358}
\shortauthors{Bischoff-Kim}
\usepackage{graphicx}
\usepackage{array}
\usepackage{epsfig}
\usepackage[outdir=./]{epstopdf}
%\usepackage{ulem}
%\usepackage{booktab}
%\usepackage{natbib}

%\bibliographystyle{natbib}

\begin{document}

\title{Asteroseismology of GD358 with complex C/O core profiles}

\author {Agn\'es~Bischoff-Kim\altaffilmark{1},
J.~L. Provencal\altaffilmark{2,3},
M.~H.~Montgomery\altaffilmark{3,4},
Samuel~T.~Harrold\altaffilmark{4},
B.~Howard\altaffilmark{3},
W.~Strickland\altaffilmark{5},
D.~Chandler\altaffilmark{5},
D.~Campbell\altaffilmark{5},
A.~Arredondo\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~P.~Russell\altaffilmark{5},
D.~Doyle\altaffilmark{5},
A.~Brickhouse\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~Peters\altaffilmark{5},
A.~V.~Kusakin\altaffilmark{6},
A.~V.~Sergeev\altaffilmark{7},
M.~Andreev\altaffilmark{7},
A.~Maksim\altaffilmark{7},
S. Velichko\altaffilmark{7}
R.~Janulis\altaffilmark{8},
F.~Ali\c cavu\c s\altaffilmark{9},
N. Horoz\altaffilmark{9},
S.~Zola\altaffilmark{10,11},
W.~Og{\l}oza\altaffilmark{10,11},
D.~Koziel-Wierzbowska{10,11},
T.~Kundera\altaffilmark{10,11},
D. Jableka\altaffilmark{10,11},
B. Debski\altaffilmark{10,11},
S. Meingast\altaffilmark{12},
}
\altaffiltext{1}{Penn State Worthington Scranton, Dunmore, PA 18512; axk55@psu.edu}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy
Newark, DE 19716; jlp@udel.edu}
\altaffiltext{3}{Delaware Asteroseismic Research Center, Mt. Cuba Observatory,
Greenville, DE 19807}
\altaffiltext{4}{Department of Astronomy, University of Texas, Austin, TX 78712;
mikemon@rocky.as.utexas.edu}
\altaffiltext{5}{Meyer Observatory and Central Texas Astronomical Society, 209
Paintbrush, Waco, TX 76705; chandler@vvm.com}
\altaffiltext{6}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
\altaffiltext{7}{Ukrainian National Academy of Sciences, Main Astronomical
Observatory, Golosiiv, Kiev 022 252650; sergeev@terskol.com }
\altaffiltext{8}{Institute of Theoretical Physics and Astronomy, Vilnius
University, Vilnius, Lithuania; jr@itpa.lt}
\altaffiltext{9}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
\altaffiltext{10}{Astronomical Observatory of the Jagiellonian University, ul. Orla
171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
\altaffiltext{11}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
\altaffiltext{12}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}

\clearpage
\newpage

\begin{abstract}
We report on ......
\end{abstract}

\keywords{Stars: oscillations --- Stars: variables: general --- white dwarfs}

\section{Astrophysical Context}
White dwarfs are the end product of evolution for around 98\% of the stars in our Galaxy. 
Buried in their interiors are the records of physical processes that take place during 
earlier stages in the life of the star. Nuclear reaction rates during the core helium 
burning phase set the core composition of white dwarfs, while the relative time spent 
burning hydrogen and helium during the asymptotic-giant-branch (AGB) phase and mass-loss 
episodes determine the thickness of the helium layer \citep{Lawlor06,Althaus05}. Helium 
atmosphere white dwarfs (DBs) comprise roughly 20\% of the population of field white 
dwarfs, with most of the remaining 80\% consisting of their hydrogen atmosphere (DA) 
cousins. The bifurcation into two spectral classes is thought to occur during post-AGB 
evolution when, in some cases, a very late thermal pulse burns off the residual hydrogen 
in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
are then supposed to return to the white dwarf cooling track as PG 1159 stars, which are 
widely believed to be the precursors of most DB white dwarfs. DBs are found to pulsate at 
effective temperatures ranging between 21,000 K and 28,000 K \citep{Beauchamp99, Castanheira05}.

The subject of this paper, GD358 (V777 Her) is the brightest ($m_{\rm v}=13.7$) and best 
studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
instability strip (\teff = , \logg =). GD358's pulsation spectrum contains a series of 
independent modes, many with complex multiplet structure.  Models involving magnetic 
fields have been proposed to explain that structure \citep{Montgomery10}. Of importance for
this work is the fact that the spacing of the multiplets is consistent with theoretical 
predictions for a series of $l=1$ modes \citep{Provencal09}.

Paradoxally, among the DBVs that have enough detected periods to be fitted 
asteroseismically, GD358 is the only one that has not been analyzed using the complex 
C/O profiles adapted and parameterized from stellar evolution calculations
([e.g.][]\citet{Salaris97,Althaus05}). The most recent fits of GD358 \citep{Metcalfe03c} were 
performed using 11 observed modes and simple models where the oxygen abundance 
drops linearly from its central value to zero.

Pulsating white dwarfs do not pulsate in all their available modes at all times.  
We have maintained an active observing program of this complex star in an effort 
to identify additional frequencies. These new observations have identified additional 
periods in GD358's pulsation spectrum, bringing the total known modes to 15. Thirteen of 
these modes belong to a consecutive $\ell=1$ sequence, the longest sequence observed 
in a DBV. This sequence is critical to constrain the asteroseismic fits and better define the
limitations of high precision white dwarf asteroseismology.

We present a new detailed asteroseismic analysis of GD358, taking advantage of 
its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
define the limits of high precision white dwarf asteroseismology.  Our goals are two-fold.  
First, we will incorporate advanced asteroseismic models to explore parameter space 
\citet{BishoffKim14}. For example, the even period spacing observed in GD358's 
pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
magnitude of the spacing is expected to be related to how compressible the stellar 
interior is. The compressibility of the interior should be inversely proportional to the 
effective temperature. A hotter object would be less compact. On the other hand, a more 
massive model will have a higher density and be less compressible. These properties lead 
to distinguishable features of the models in the mass versus effective temperature 
parameter plane. We can explore such features with GD358 because we have a long, 
confirmed, single $\ell$ sequence of modes of higher radial order.

Secondly, the present analysis allows us to place GD358 in the context of stellar evolution. 
According to the models, the precursors of DBs emerge from the born-again phase with 
envelopes containing a nearly uniform mixture of helium (He), carbon (C), and oxygen (O) 
out to the photosphere \citep{Dreizler98,Herwig99}. As the PG 1159 stars cool, the helium 
diffuses upward and gradually accumulates to form a chemically pure surface layer. Through 
the DBV instability strip, this process is still ongoing so that instead of a pure helium 
layer surrounding the carbon and oxygen core, one has a region where the carbon and helium 
are still mixed. This leads to a double layered structure, with the pure He surface layer 
overlying the remainder of the uniform He/C/O envelope, all above the degenerate C/O core. 
A key prediction of the diffusion models is that, for a given stellar mass, the pure He 
surface layer will steadily grow thicker as the DB star cools.  GD358 is the fourth DBV 
we can use to check this theory. The other three DBVs 
(\citet{Bishoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture consistent with 
the diffusion calculations, with the hotter best fit models having thinner pure helium 
layers. With GD358, we seek to confirm this trend qualitatively.

In Section \ref{data}, we present our new observations and outline the data reduction process.  
In Section \ref{freq}, we establish the framework for frequency identification, and present the 
list of frequencies used for the asteroseismic investigation.  Section \ref{aster} outlines the 
asteroseismic investigation, and .....

\section {New Observations and Data Reduction}\label{data}

GD358 was discovered in 1982 \citep{Winget82} and has been the target of the Whole 
Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
2007-2015 (Table \ref{journal}. Each season of observations was obtained as part of 
multisite WET campaigns.

Standard procedure for WET observations calls for observers to transfer raw images and 
calibration files to WET headquarters for analysis at the end of each local night. CCD 
data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
were obtained with different CCD photometers, each with distinct effective bandpasses. 
We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
reduce extinction effects. We corrected each image for bias and thermal noise, and 
normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
described by \citet{Dalessio10} was performed on each image, utilizing a range of 
aperture sizes for the target and comparison stars. For each individual nightly run, we 
chose the combination of aperture size and comparison star(s) producing the highest 
signal/noise light curve.

We used the WQED pipeline \citet{wqed} to examine each nightly light curve for photometric 
quality, remove outlying points, divide by suitable comparison stars, and correct for 
differential extinction. Our observational technique is therefore not sensitive to 
oscillations longer than a few hours. The result is a series of light curves 
with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
representation of the fractional intensity of modulation (1 mmi $\approx$1 mmag). We present
our Fourier transforms (FTs) in units of modulation amplitude 
($1\sim mma=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1\sim ppt$).

The final reduction step is to combine the individual light curves (Figure \ref{tersk}) to produce 
complete light curves for GD358 for each observing season. We assume GD358 oscillates about 
a mean light level. This assumption allows us to carefully assess overlapping segments from 
different telescopes and identify and correct any vertical offsets. As discussed in detail 
in \citet{Provencal09}, we find no significant differences between the noise levels of 
amplitude spectra using: 1) the combination of all light curves including overlapping 
segments from different telescopes, 2) the combination of light curves where we retain 
only higher signal to noise observations in overlapping segments and 3) combining all light 
curves using data weighted by telescope aperture.

\begin{figure}
\epsscale{0.7}
\plotone{terskol}
\caption{Light curve of GD358 obtained with the Peak Terskol 2.0m.  Each point corresponds 
to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
\label{tersk}
}
\end{figure}

The result is a series of new light curves for each observing season between 2007 and 2015. 
2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 2010 201.3 hrs, 2011 
401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. Our coverage is 
not complete, and this incompleteness produces spectral leakage in the amplitude spectra. 
To quantify this, we sampled single sinusoids using exactly the same times as the original 
data for each season. The resulting amplitude spectrum, or ``spectral window'', is the 
pattern produced in the FT by a single frequency. The FTs for 2010, 2011, and 2014 
are given in Fig.~\ref{fts}.

\begin{figure}
\plotone{gd358multidft}
\caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz are combination 
frequencies discussed in Section \ref{analysis} (right arrow, blue). 
(A color version of this figure is available in the online journal.)
\label{fts}
}
\end{figure}

\section{Frequency Identification}\label{freq}

Our goal is to compile a complete list of GD358's observed independent and combination frequencies 
to be used in a comprehensive asteroseismic analysis. GD358 is known for large scale changes in 
amplitudes and small but not insignificant frequency variations on a variety of timescales 
\citep{Provencal09}.  The amplitude and frequency variations evident in Fig.~\ref{fts} will 
produce artifacts in FTs, greatly complicating any frequency analysis.  
We reanalyzed all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
as well as our new observations to insure continuity in methodology.  We use 
{\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
select statistically significant peaks in each FT.  As discussed in \citet{Provencal12}, 
we adopt the criterion that a peak must have an amplitude at least four times greater than the 
average noise level in the given frequency range. We define ``noise'' as the frequency-dependent 
average amplitude after prewhitening by the dominant frequencies. This is a conservative estimate, 
as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies \citep{Provencal09}.  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
archival data is presented in Figure 3 of \citet{Provencal09}. To confirm our uncertainty 
estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
This routine generates a set of light curves using the original times, the fitted frequencies and 
amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
are consistent with our average noise estimates.

\begin{figure}
\plotone{noise}
\caption{A comparison of the average noise as a function of frequency for the 2007-2015 observing 
seasons.  Each data set was prewhitened by its dominant frequencies.  The noise levels for each 
season are somewhat different.  This must be taken into account during frequency analysis.  
\label{noise}
}
\end{figure}

Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
modulation is given in \citep{Provencal09}. Our final identifications of independent frequencies
detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.

\section{Frequency Analysis}\label{analysis}

\subsection{Frequencies Distribution}

Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
important ways.  First, frequencies detected in a given observing season are not found 
in all observing seasons. Asteroseismology is based on the assumption that the available pulsation
frequencies are linked to stellar structure.  Since we are fairly certain that GD358's internal structure 
does not change on the timescales of the observations, we can assume that GD358 excites 
different subsets of its available pulsations at different times. While this is a common phenomenon
seen in white dwarf pulsators, the selection mechanism remains mysterious. The best way to 
determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
from multiple observing seasons as outlined in \citep{Kleinman98}.

\begin{figure}
\epsscale{0.8}
%\plottwo{gd358multif_2015.eps}{gd358multi.eps}
%\centering{
%\includegraphics[width=1.0]{gd358multif_2015.eps}
%}
\plotone{gd358multif_2015.eps}
\caption{A schematic representation of GD358's pulsation modes for all available data between
1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
\muHz (400 and 1000 s) are of particular importance for this work. (A color version of this 
figure is available in the online journal.)
\label{schematic}
}
\end{figure}

Figure~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
available data. The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz (1100 and 400 s). We interpret each band to represent a single radial overtone in GD358. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands. The lower frequency band widths are 
most likely the result of amplitude and/or frequency modulation that obscures any underlying 
signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300 {\em{right}}
 and 2360 \muHz {\em{left}}. The 1300 \muHz band shows no multiplet structure, unlike the 2360 \muHz
 band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
 $l=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Figure \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) \kicnsp 4552982, 
in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. Although the 
observational timebases are quite different (20 months for \kicnsp 4552982 vs 30 years for GD358), our 
data presents the opportunity to investigate this for a DB pulsator.  We measured the width of each of 
GD358's band. We define ''width'' as the difference between the lowest and highest frequency 
detected in each band. Figure \ref{thick} presents the results. The widths of GD358's bands are 
commensurate with those found in \kicnsp 4552982.  We also find a general increase in width with 
decreasing frequency (increasing period), until we reach the mode at 1238\muHz (807 s). This band has 
a width at least twice as wide as any other.  What is different about this mode???

\begin{figure}
 \epsscale{0.8}
 \plotone{modethick.eps}
 \caption{Width of each bank of power in Fig.~\ref{schematic}. We find an overall increase 
 in band thickness with decreasing frequency (increasing period).  The band at 807~s has a width
 at least twice as large as other bands.  
 \label{thick}}
\end{figure}

\subsection{Mode Identification}

GD358 is extensively studied \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}.  Our current 
work has produced a well defined sequence of modes. The previous identification of these modes as 
a series of $l$=1 radial overtones is based mostly on the pulsation frequency distribution 
and limited spectroscopic analysis \citep{Kotak02, Castanheira05}. It is important to further 
investigate these identifications as we initiate an indepth asteroseismic investigations.

GD358's combination frequencies provide a tool by which we can bolster $l$ identifications. 
Combination frequencies are typically observed in the FTs of moderate to large amplitude pulsators.  
They are identified by their exact numerical relationships with parent frequencies.  
The combinations themselves are not independent, but result from nonlinear effects associated 
with the surface convection zone \citep{Brickhill92, Brassard95, Wu01, Ising01}.  
\citet{Wu01} lays the groundwork, showing that observed amplitudes of the combination 
frequencies depend on geometric factors such as the $(l,m)$ indices of the parents and the 
inclination of the pulsation axis to the line of sight.

The methods outlined in \citet{Provencal12} and \citet{Montgomery10} work best when applied to 
larger amplitude frequencies detected in high signal to noise data sets such as provided by 
extensive WET runs.  The primary reason for this is that combination frequencies are lower 
amplitude than their parents, and so are more difficult to detect in sparse data.  We chose 
the 1990, 1994, 2006, 2010, 2011, and 2014 observing seasons, and looked at pulsation 
frequencies with amplitudes above 10 mma.

Figure~\ref{amps} shows the resulting probability distribution of $l$ and $m$ values for the 1735.96 \muHz
frequency detected in 2014.

\begin{figure}
 \epsscale{0.8}
 \plotone{modeamps.eps}
 \caption{Probability distribution (from 0 to 1) of $l$ and $m$ values for the 1735.96 variation detected in 
 2014.  The solutions are from individual simulations with $Res_{rms}<9.5e-06$. The amplitudes of the 
 observed combination frequencies argue that this is $l$=1, $m$=1.  
 \label{modeamps}
 }
\end{figure}

Finally, given the $l$=1 identification, but the lack of definite multiplet structure, the best way to 
determine the l=0 component for each band is simply to average the frequencies in the bands.  We experimented
with numerous weighting techniques, and determined there is no significant difference in our solutions.  
Our final frequency identification for each band is given in Table~\ref{tl}.

\section{Pulsational properties}
\label{prop}

\section{Asteroseismic fitting}\ref{astero}
\label{fitting}

The basic method in our asteroseismic fitting consists of calculating grids of white dwarf models and 
running a fitting subroutine to match the periods of the models ($\rm P_{calc}$) with the observed 
periods and calculated residuals using the usual formula

\begin{equation}
\label{fiteq1}
\rm \sigma_{RMS} = \sqrt{\frac{\sum_{1}^{n_{obs}} {(P_{calc}-P_{obs})^2}}{n_{obs}}},
\end{equation}

\noindent where $\rm n_{obs}$ is the number of periods present in the pulsation spectrum.

\subsection{The Models}
\label{models}

To compute our models, we used the White Dwarf Evolution Code (WDEC). The WDEC evolves hot 
polytrope models from temperatures above 100{,}000~K down to the temperature of our choice. 
Models in the temperature range of interest for the present study are thermally relaxed 
solutions to the stellar structure equations. Each model we compute for our grids is the result 
of such an evolutionary sequence. The WDEC is described in detail in \citet{Lamb75} and 
\citet{Wood90}. We used smoother core composition profiles and implemented more complex profiles 
that result from stellar evolution calculations \citep{Salaris97}. We updated the envelope 
equation of state tables from those calculated by \citet{Fontaine77} to those given by 
\citet{Saumon95}. We use OPAL opacities \citep{Iglesias96} and plasmon neutrino rates 
published by \citet{Itoh96}.

DBVs are younger than their cooler cousins the DAVs. Time-dependent diffusion calculations 
\citep[e.g.][]{Dehner95,Althaus05} show that at 24{,}000~K, a typical temperature for a DBV, 
the carbon has not fully settled into the core of the star yet. We expect the helium layer to 
be separated into a mixed He/C layer with a pure He layer on top, as shown in Fig. \ref{ffit1}. 
Following  \citet{Metcalfe05a}, we adopted and parameterized this structure in our models.

\begin{figure}
%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
%  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
\plotone{ffit1.eps}
\caption{
{\em Upper panel:} Chemical composition profiles of our models to illustrate the parameterization 
of the internal chemical structure. The center of the model is to the left and the surface to 
the right.  $q=2$ corresponds to $M_r = 0.99 \: M_*$. The vertical axis shows fractional abundances. 
{\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). Each 
chemical transition leads to a bump in the \bvf frequency. \label{ffit1}
}
\end{figure}

\subsection{Initial grid search}
\label{grids}

In our asteroseismic fits, we initially varied six parameters; the effective temperature, 
the mass and four structure parameters. There are two parameters associated with the shapes 
of the oxygen (and carbon) core composition profiles: the central oxygen abundance ($X_o$) and 
the edge of the homogeneous carbon and oxygen core ($q_{\rm fm}$, as a fraction of stellar mass. 
For envelope structure, $M_{\rm env}$ marks the location of the base of the helium layer 
and $M_{\rm He}$ the location where the helium abundance rises to $1$ (see Figure \ref{ffit1}). 
$M_{\rm env}$ and $M_{\rm He}$ are mass coordinates, defined as e.g. 
$M_{\rm env} = -\log(1 - M(r)/M_*)$, where $M(r)$ is the mass enclosed in radius r and 
$M_*$ is the stellar mass.

We started with a master grid (table \ref{fitt1}) chosen so that it covered all relevant 
area of parameter space and had sufficient resolution, based on previous experience 
\citep{Bischoff-Kim11a,Bischoff-Kim14} to find any region of local minimum in the fitness parameter, 
but was small enough to be computationally manageable. The master grid involved the computation 
of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
modes. The results of this initial fit are shown in the left panel of figure \ref{ffit2}.

\subsection{Asymptotic period spacing}
\label{periodspacing}

Before we refine the period-by-period fitting optimization, it is worth stepping back and consider 
what we can learn from the average period spacing of GD358. The average period spacing provides a 
useful asteroseismic measure of the mass and temperature of the star, independent of the details of 
internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
given by (Unno et al. 1989)

\begin{equation}
\label{fiteq2}
\Delta P = \frac{\pi}{\ell(\ell + 1)^{1/2}}\left[\int_{r_1}^{r_2}\frac{N}{r}dr\right]^{-1},
\end{equation}

\noindent
where $r_1$ and $r_2$ are turning points of the mode and N is the Brunt-V\"{a}is\"{a}l\"{a} frequency. 
The asymptotic period spacing is $\ell$ dependent, with higher $\ell$ modes having smaller spacing. 
In the case of GD 358, we have a single $\ell=1$ sequence so we only need to worry about the dependence 
of the asymptotic period spacing on the \bvf frequency. Much if not all of GD 358's pulsation 
spectrum is in the asymptotic limit, because the shortest period observed is a $k=8$ mode.

The dependence of $\Delta P$ on the \bvf frequency leads to higher mass and lower temperature models 
having a smaller period spacing (their interior is less compressible). This effect appears in asteroseismic 
fitting of white dwarfs and also sdB stars as a ubiquitous diagonal trend in contour maps of the quality 
of the fits in the mass-effective temparature plane \citep[e.g][]{Bischoff-Kim14,Castanheira09,Charpinet08}. 
One requirement for the periods of the model to match the observed periods is that the average period spacing 
in the models matches the average period spacing in the observed pulsation spectrum. If a good match occurs 
for a given mass and effective temperature, then models with lower mass but higher effective temperature 
will also match well.

We can use the sequence of 13 consecutive $\ell=1$ modes we have with GD 358 to calibrate our models. 
Using the $ell=1$ sequence of modes, we compute an average period spacing of 39.08 seconds. We call 
this $\Delta P_{\rm obs}$. For each model in the master grid, we compute an asymptotic period spacing 
($\Delta P_{\rm calc}$). This asymptotic period spacing is calculated by first discarding the first 
10 modes. The exact value of 10 is somewhat arbitrary, but it is chosen so that the modes we use in 
our computation are indeed in the asymptotic limit. The higher $k$ modes show weaker trapping than the 
lower $k$ modes. We then fit a line through the set ($k_i$,$P_i$). The slope gives us the asymptotic 
period spacing in the model. We also calculate the residuals of the fits and as an additional check, 
discard the models that have residuals above a certain limit. The limit is chosen by checking the procedure 
by eye on a few models.

We show a contour map of the location of the models that best match the average period spacing of 
39.08 seconds in Fig. \ref{ffit1}, right panel. We place it side by side with a contour map showing 
the location of the best fit model in the same region of parameter space, based on the master grid 
fitting described in section \ref{grids}. Note how the best fit model falls right within the valley 
where the period spacings between GD358 and the models match. This should come as no surprise, as in 
order for 15 periods to fit reasonably well, the model period list should have a spacing similar to 
that of the observed period spectrum. It is also somewhat comforting to find that the spectroscopic 
data point also falls within the swath where the period spacings match (though the best fit model 
based on the master grid search is further down the valley).

%  \includegraphics[width=1.0\columnwidth]{ffit2.eps}
\begin{figure}
\epsscale{0.7}
\plotone{ffit2.eps}
\caption{
{\it Left panel}: Contour map showing the location of the best fit models. The quantity plotted in 
the mass-effective temperature plane is the fitness parameter defined in equation \ref{fiteq1}. 
The scale is in seconds. {\it Right panel}: Contour map of the difference between the average 
periods spacing determined from GD 358's periods and the asymptotic period spacing of the models, 
in the mass-effective temperature plane. The scale is in 10s of seconds, so the worse matches 
pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 2 \; \rm s$. \label{ffit2}
}
\end{figure}

One can fit simultaneously the average period spacing and the individual periods 
formally while performing the fits by using some prescription to calculate the fitness parameter 
{Travis,canadians?}. This leads to a more complex relation than defined in equation \ref{fiteq1}. 
Note that the period spacing is a much weaker constraint than the individual period fit. 
If one takes 4 seconds as an upper limit for fitness, that includes a single point in the 
period-by-period fit plot (left panel in Fig \ref{ffit2}), but the entire parameter plane 
for the average period spacing fit plot (right panel). We bypass the difficulty of 
assigning proper weights to each constraint by taking the average period spacing fit into 
account as an initial step to refine our fits. We refine our fits by calculating models on 
a higher resolution grid that fall within the region defined by the two diagonal lines shown 
in the right panel of figure \ref{ffit2}, then performing a period-by-period fit using 
equation \ref{fiteq1}.

%If we now look for the models that have $\Delta P_{\rm calc} = \Delta P_{\rm obs} = 39.08$ s 
%and plot their mass and effective temperature, we do recover the expected diagonal trend 
%(Fig \ref{ffit}). We can use the asymptotic period spacing to calibrate our models. Before 
%we seek the detailed chemical make-up by performing period-by-period matching, we can 
%test whether the bulk properties of our models are consistent with our observations of the 
%stars. With spectroscopy, we can obtain a measurement of the effective temperature, and 
%with the addition of a mass-radius relation, the star mass. For GD 358, we use results 
%quoted in XXX and XXX. Both (all X) values are included on Fig. \ref{f3}. We see that our 
%trend of best match between the calculated and the observed average period spacings goes 
%right through the data points. GD 358 is the first DBV for which we are able perform this 
%test. Our models have bulk properties that appear consistent with at least one real star. 
%We confidently move on to our period-by-period fitting.

\subsection{Determining the best grid resolution for refined fits}

Having determined a more restricted region of parameter space to search for 
the best fit models, we now turn to the question of how fine we need to 
make our refined grid. We want to have a high enough resolution grid that 
we can be sure we captured a true minimum, but on the other hand, there are 
computational limitations to how many models we can afford to calculate, 
save, and process.

One way to gain a sense of how fine the grid needs to be is to make single 
parameter cuts through parameter space. Fig.  \ref{ffit3} shows such a cut 
for master grid models. The plot was made by fixing 5 of the 6 parameters 
to their best fit value 
($M_*=0.590 M_{\odot}$, $M_{\rm env}=2.40$, $M_{\rm He}=5.15$, $X_o=0.45$, and $q_{\rm fm}=0.15$). 
We allowed the effective temperature to vary through the entire range 
considered for the master grid (table \ref{fitt1}). One can see that the 
fits are generally poor, though they do seem to settle to a minimum in a 
smooth way. Except for the striking anomaly at 26,600~K. Upon further 
investigation, we discovered that anomaly to be due to a single period in 
the pulsation spectrum: the 968~s mode. In the model, that mode appears 
highly sensitive to some parameters, and in a non-continuous way.

\begin{figure}
\epsscale{0.7}
\plotone{ffit3.eps}
%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
%  \includegraphics[width=0.9\columnwidth]{ffit3.eps}
\caption{
Dependence of the fitness parameter on effective temperature alone based on 
the master grid of models. \label{ffit3}
}
\end{figure}

This is unsettling, as it is easy to see that one might miss the best fit 
models if the grid is not fine enough. In order to quantify "fine enough", 
we ran systematic scans, computing models with 5 parameter fixed and allowing 
the 6th parameter to vary in very fine steps. We went all the way down in 
step sizes to $\Delta {\rm T_{eff}}=1$~K, $\Delta M_*=0.1 M_\odot$, 
$\Delta M_{\rm env}= \Delta M_{\rm He}=1$, $\Delta X_o=1$, and $\Delta q_{\rm fm}=0.1$. 
Results for 4 different parameters are shown in Fig \ref{ffit4}. The figure 
includes zooms to regions of interest. Other modes also exhibit a behavior 
similar to the 968~s mode, in different regions of parameter space. For instance, 
the jumps in $\sigma_{\rm RMS}$ for $q_{\rm fm}$ between 0.3 and 0.4 are due 
to sudden changes in the 854.5 and 902.5~s modes.

Regardless of the behavior of individual modes in the models as the parameters vary, 
we can assert from the test above what step sizes will allow us to minimize our risk 
of missing a minimum. We settled on optimal step sizes of 
$\Delta {\rm T_{eff}}=20$, $\Delta M_*=0.2$, $\Delta M_{\rm He}=20$, 
$\Delta X_o=20$, and $\Delta q_{\rm fm}=1$ for our refined grid. To offset 
the computational cost, we fixed $M_{\rm env}$ to a canonical value of 
2.80 \citep{Dehner95}. It is clear from the second panel in Fig. \ref{ffit4} 
that there is only a weak dependence of the fits on that parameter.

\begin{figure}
\epsscale{0.7}
\plotone{ffit4.eps}
%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
%  \includegraphics[width=0.9\columnwidth]{ffit4.eps}
\caption{
  \label{ffit4}
Dependence of the fitness parameter on different parameters. The 5 parameters not 
shown on the horizontal axis in each plot are held to fixed values corresponding 
to the best fit model. \label{ffit4}
}
\end{figure}

\section{Results of the period fitting}

\section{Discussion and Conclusions}
\label{discussion}

Lessons learned: how fine a grid must be. CAUTION with pipeline fitting. we learn that one must 
exert extreme caution in any automated pipeline-type fitting of white dwarf stars.
Asymptotic theory \\
We recover the trend in mass/teff plane \\
We confirm the weak dependence on 4 interior parameters. \\
We calibrated our models.

\acknowledgments

{\it Facilities:} \facility{MCAO:0.6m ()}, \facility{Struve()},
\facility{KPNO:2.1m ()}, 
\facility{}, \facility{BOAO:1.8m ()}, \facility{Lulin:1.8m ()},
\facility{Beijing:2.16m ()}, \facility{Maidanek:1.5m ()}, \facility{Peak Terskol}

\bibliographystyle{apj}
\bibliography{index_f}

\clearpage

\begin{deluxetable}{rrrrr}
\tablecolumns{5}
\tabletypesize{\small}
\tablewidth{0pc}
\tablecaption{}
\tablehead{
\colhead{Run Name} & \colhead{Telescope} & \colhead{Detector} & \colhead{Date} & \colhead{Length}\\
\colhead{} & \colhead{} & \colhead{} & \colhead{} & \colhead{(hrs)}
\label{journal}}
\startdata
\input{journaldata.tex}
\enddata
\end{deluxetable}

\clearpage

\input{1982freq.tex}
\clearpage
\input{2011freq.tex}
\clearpage
\input{gd358freqtab.tex} % label is gd358freq
\clearpage
\input{fitt1} % label is fitt1
\clearpage
%\begin{thebibliography}{}
%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

%\end{thebibliography}

\end{document}

### 2016-02-08 msnew.tex
Made changes to msnew.tex

@@
 \usepackage[outdir=./]{epstopdf}
+\usepackage{deluxetable}
 %\usepackage{ulem}
@@
 
-\section{Pulsational properties}
-\label{prop}
-
 \section{Asteroseismic fitting}\ref{astero}
@@
 
-\begin{figure}
-%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
-%  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
-\plotone{ffit1.eps}
-\caption{
-{\em Upper panel:} Chemical composition profiles of our models to illustrate the parameterization 
-of the internal chemical structure. The center of the model is to the left and the surface to 
-the right.  $q=2$ corresponds to $M_r = 0.99 \: M_*$. The vertical axis shows fractional abundances. 
-{\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). Each 
-chemical transition leads to a bump in the \bvf frequency. \label{ffit1}
-}
-\end{figure}
-
 \subsection{Initial grid search}
@@
 of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
-modes. The results of this initial fit are shown in the left panel of figure \ref{ffit2}.
+modes. A fitness map of this initial fit are shown in the left panel of figure \ref{ffit2}, and the parameters of the best fit model are listed in table \ref{fitt1}.
 
@@
 of the asymptotic period spacing on the \bvf frequency. Much if not all of GD 358's pulsation 
-spectrum is in the asymptotic limit, because the shortest period observed is a $k=8$ mode.
+spectrum is close to the asymptotic limit, because the shortest period observed is a $k=8$ mode.
 
@@
 One can fit simultaneously the average period spacing and the individual periods 
-formally while performing the fits by using some prescription to calculate the fitness parameter 
-{Travis,canadians?}. This leads to a more complex relation than defined in equation \ref{fiteq1}. 
+formally while performing the fits by using some prescription to calculate the goodness of fit. 
+This leads to a more complex relation than defined in equation \ref{fiteq1}. 
 Note that the period spacing is a much weaker constraint than the individual period fit. 
@@
 a higher resolution grid that fall within the region defined by the two diagonal lines shown 
-in the right panel of figure \ref{ffit2}, then performing a period-by-period fit using 
+in the right panel of figure \ref{ffit2} (covering the effective temperature range 25,000~K-27,500~K, then performing a period-by-period fit using 
 equation \ref{fiteq1}.
@@
 \subsection{Determining the best grid resolution for refined fits}
+\label{refinedfits}
 
@@
 for master grid models. The plot was made by fixing 5 of the 6 parameters 
-to their best fit value 
-($M_*=0.590 M_{\odot}$, $M_{\rm env}=2.40$, $M_{\rm He}=5.15$, $X_o=0.45$, and $q_{\rm fm}=0.15$). 
+to the best fit values of the best initial fit (see table \ref{fitt1}).
 We allowed the effective temperature to vary through the entire range 
@@
 
+The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in table \ref{gd}.
+The goodness of fit of the model is $sig_RMS = 4.22 s$.
+In Fig.
+\ref{ffit1}, we show the interior structure of the best fit model, with the corresponding \bvf frequency profile.
+
+\begin{figure}
+%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
+%  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
+\plotone{ffit1.eps}
+\caption{
+{\em Upper panel:} Chemical composition profiles of the best fit model.
+The center of the model is to the left and the surface to the right.
+$q=2$ corresponds to $M_r = 0.99 \: M_*$.
+The vertical axis shows fractional abundances.
+{\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). \label{ffit1}
+}
+\end{figure}
+
+\subsection{Validation of the fitting method}
+
+With what we have discovered in section \ref{refinedfits}, it is only natural to be concerned about whether we have truly found a best fit.
+We performed a simple test to validate our fitting method, which consisted of using the exact same procedure to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that were very close to the best fit model.
+We used the period list for a model with parameters ${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, fixing $M_{\rm env}$ to -2.80, including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
+
+We first performed a fitting of the periods using the master (coarse) grid described in section \ref{grids}.
+This placed the best fit model in the appropriate region of parameter space.
+Then we refined our fits, using the grids described at the end of section \ref{periodspacing}.
+We are able to recover the best fit parameters adequately, with the top 10 best fit models having parameters ${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 10 fits, and $q_{\rm fm}=0.175 \pm 0.5$.
+The top 10 best fits have \sigrms $\sim$ 0.5~s.
+We remind the reader that the step sizes in the second phase of the fitting are 20~K for ${\rm T_{eff}}$, 0.2 for $M_{\rm He}$, 0.2 for $X_o$, and 0.01 for $q_{\rm fm}$.
+
 \section{Discussion and Conclusions}
 \label{discussion}
+
+In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness number.
+This is due to the fact that some periods can change values drastically for a small change in a given parameter.
+The phenomenon is only semi-chaotic, as the period will oscillate between two values.
+This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
+Any search algorithm that uses a small enough mesh should be able to find the minimum.
+This phenomenon likely became apparent while fitting GD358 because with that star, we are fitting a long consecutive sequence of modes of the same ell.
+
+We have performed and published a preliminary fit of the star (Hawaii proceedings), where we found a temperature of 23,600 K, a mass of 0.605 $M_\odot$, \menv = -2.40, \mhe = -5.20, a central oxygen abundance of 0.99, and \qfm = 0.50.
+In the preliminary fits, the period list was not finalized and we did not include the 1065.260 s mode, because it was difficult to fit and we did not have a positive ell identification for the mode.
+It might be disheartening to observe such a big difference in the best fit parameters by just including or excluding one mode out of 15, but it is worth noting that the thickness of the pure helium layer was not affected much by the inclusion or exclusion of the 15th mode and refinements done in the search in this work.
+We emphasize again that in the final stages of our fitting for this work, we fixed the envelope mass to -2.80.
+
+In section \ref{periodspacing}, we discussed the degeneracy in the determination of the mass and effective temperature parameters.
+That degeneracy means that a unique determination of effective temperature and mass is not always possible.
+The fits are also marginally sensitive to the central oxygen abundance.
+What is surprising is the big difference in the determination of the location of the edge of the homogeneous C/O core from our preliminary fits to the refined fits presented in this paper.
+If we take the best fit model from the preliminary work and include the 15th period when calculating the fitness number, the quality of the fit becomes significantly worse (2.84 s to 5.12 s).
+We would not expect a k=24 mode to be strongly trapped in the core, quite the contrary.
+This could be due to a core-envelope symmetry \citep{Montgomery03}, but more detailed studies would be required to make a more definitive statement.
+We should also keep in miind that the period lists used in the fits were close but not identical.
 
@@
 \clearpage
-\input{gd358freqtab.tex} % label is gd358freq
+\input{gd358fit.tex} % label is gd358freq
 \clearpage

### 2016-02-08 msnew.tex
Fixed some typos in tables that would not compile. Also edited msnew.tex so that now it does compile.

@@
 \usepackage{graphicx}
-\usepackage{array}
+%\usepackage{array} %Don't activate doesn't play nice with deluxe tables!!!
 \usepackage{epsfig}
 \usepackage[outdir=./]{epstopdf}
-\usepackage{deluxetable}
 %\usepackage{ulem}
@@
 
-\author {Agn\'es~Bischoff-Kim\altaffilmark{1},
+\author {Agn\`es~Bischoff-Kim\altaffilmark{1},
 J.~L. Provencal\altaffilmark{2,3},
@@
 First, we will incorporate advanced asteroseismic models to explore parameter space 
-\citet{BishoffKim14}. For example, the even period spacing observed in GD358's 
+\citet{BischoffKim14}. For example, the even period spacing observed in GD358's 
 pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
@@
 we can use to check this theory. The other three DBVs 
-(\citet{Bishoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture consistent with 
+(\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture consistent with 
 the diffusion calculations, with the hotter best fit models having thinner pure helium 
@@
 
+\input{gd358fit.tex} % label is gd358freq
+
 We started with a master grid (table \ref{fitt1}) chosen so that it covered all relevant 
@@
 \startdata
-\input{journaldata.tex}
+%\input{journaldata.tex}
 \enddata
@@
 
-\input{1982freq.tex}
+%\input{1982freq.tex}
 \clearpage
-\input{2011freq.tex}
+%\input{2011freq.tex}
 \clearpage
-\input{gd358fit.tex} % label is gd358freq
 \clearpage

### 2016-02-08 githubcommands.sh

@@ -1,0 +1,11 @@
+#/bin/bash
+
+git add --all
+git commit
+git push origin master
+
+#list updates about local directory
+#git branch -v
+
+#list remote directories attached to local directory
+#git remote -v

### 2016-02-11 msnew.tex
housekeeping

@@
 B. Debski\altaffilmark{10,11},
-S. Meingast\altaffilmark{12},
+S. Meingast\altaffilmark{12}
 }
@@
 studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
-instability strip (\teff = , \logg =). GD358's pulsation spectrum contains a series of 
-independent modes, many with complex multiplet structure.  Models involving magnetic 
-fields have been proposed to explain that structure \citep{Montgomery10}. Of importance for
+instability strip, with \teff of 24000~K and \logg of 7.8 \citep{Koester2013}. GD358's 
+pulsation spectrum contains a series of independent modes, many with complex 
+frequency structure.  Models involving magnetic fields and oblique rotation have been 
+proposed to explain that structure \citep{Montgomery10}. Of importance for
 this work is the fact that the spacing of the multiplets is consistent with theoretical 
-predictions for a series of $l=1$ modes \citep{Provencal09}.
+predictions for a series of $\ell=1$ modes \citep{Provencal09}.
 
@@
 First, we will incorporate advanced asteroseismic models to explore parameter space 
-\citet{BischoffKim14}. For example, the even period spacing observed in GD358's 
+\citep{BischoffKim14}. For example, the even period spacing observed in GD358's 
 pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
@@
 In Section \ref{freq}, we establish the framework for frequency identification, and present the 
-list of frequencies used for the asteroseismic investigation.  Section \ref{aster} outlines the 
+list of frequencies used for the asteroseismic investigation.  Section \ref{fitting} outlines the 
 asteroseismic investigation, and .....
@@
 
-Standard procedure for WET observations calls for observers to transfer raw images and 
+Standard WET procedure calls for observers to transfer raw images and 
 calibration files to WET headquarters for analysis at the end of each local night. CCD 
@@
 
-We used the WQED pipeline \citet{wqed} to examine each nightly light curve for photometric 
+We used the WQED pipeline \citep{wqed} to examine each nightly light curve for photometric 
 quality, remove outlying points, divide by suitable comparison stars, and correct for 
@@
 The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
-is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz are combination 
+is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
 frequencies discussed in Section \ref{analysis} (right arrow, blue). 
@@
 determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
-from multiple observing seasons as outlined in \citep{Kleinman98}.
+from multiple observing seasons as outlined in \citet{Kleinman98}.
 
@@
 1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
-\muHz (400 and 1000 s) are of particular importance for this work. (A color version of this 
+\muHz\ (400 and 1000 s) are of particular importance for this work. (A color version of this 
 figure is available in the online journal.)
@@
 available data. The features of asteroseismic importance are the localized bands between 900 and 2400
-\muHz (1100 and 400 s). We interpret each band to represent a single radial overtone in GD358. The bands
+\muHz\ (1100 and 400 s). We interpret each band to represent a single radial overtone. The bands
 themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
@@
 % \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
- \caption{The detailed schematic distribution of frequencies for the bands near 1300 {\em{right}}
- and 2360 \muHz {\em{left}}. The 1300 \muHz band shows no multiplet structure, unlike the 2360 \muHz
+ \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
+ and 2360 \muHz\ ({\em{left}}). The 1300 \muHz\ band shows no multiplet structure, unlike the 2360 \muHz\
  band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
- $l=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
+ $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
  (A color version of this figure is available in the online journal.)
@@
 Figure \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
-\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) \kicnsp 4552982, 
+\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) KIC4552982, 
 in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
@@
 different widths in frequency space, and that there may be astronomical significance to this. Although the 
-observational timebases are quite different (20 months for \kicnsp 4552982 vs 30 years for GD358), our 
-data presents the opportunity to investigate this for a DB pulsator.  We measured the width of each of 
-GD358's band. We define ''width'' as the difference between the lowest and highest frequency 
-detected in each band. Figure \ref{thick} presents the results. The widths of GD358's bands are 
-commensurate with those found in \kicnsp 4552982.  We also find a general increase in width with 
-decreasing frequency (increasing period), until we reach the mode at 1238\muHz (807 s). This band has 
-a width at least twice as wide as any other.  What is different about this mode???
+observational timebases and coverage are quite different (20 continuous months for KIC4552982 vs 30 
+incomplete years for GD358), our data presents the opportunity to investigate this for a DB pulsator.  
+We measured the width of each of GD358's band. We define ''width'' as the difference between the 
+lowest and highest frequency detected in each band. Figure \ref{thick} presents the results. 
+The widths of GD358's bands are commensurate with those found in KIC4552982.  We also find a general 
+increase in width with decreasing frequency (increasing period), until we reach 
+the mode at 1238\muHz\ (807 s). This band has a width at least twice as wide as any other.  What 
+is different about this mode???
 
@@
 
-GD358's combination frequencies provide a tool by which we can bolster $l$ identifications. 
+GD358's combination frequencies provide a tool by which we can bolster $\ell$ identifications. 
 Combination frequencies are typically observed in the FTs of moderate to large amplitude pulsators.  
@@
 \citet{Wu01} lays the groundwork, showing that observed amplitudes of the combination 
-frequencies depend on geometric factors such as the $(l,m)$ indices of the parents and the 
+frequencies depend on geometric factors such as the $(\ell,m)$ indices of the parents and the 
 inclination of the pulsation axis to the line of sight.
@@
 
-Figure~\ref{amps} shows the resulting probability distribution of $l$ and $m$ values for the 1735.96 \muHz
-frequency detected in 2014.
+Figure~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
+frequency as detected in 2014.
 
@@
  \plotone{modeamps.eps}
- \caption{Probability distribution (from 0 to 1) of $l$ and $m$ values for the 1735.96 variation detected in 
- 2014.  The solutions are from individual simulations with $Res_{rms}<9.5e-06$. The amplitudes of the 
- observed combination frequencies argue that this is $l$=1, $m$=1.  
+ \caption{Probability distribution (from 0 to 1) of $\ell$ and $m$ values for the 1735.96 variation detected in 
+ 2014.  The solutions are from individual simulations with $Res_{rms}<9.5^{-06}$. The amplitudes of the 
+ observed combination frequencies argue that this is $\ell=1$, $m$=1.  
  \label{modeamps}
@@
 \end{figure}
+
+Add table with all l,m ids
 
@@
 
-\section{Asteroseismic fitting}\ref{astero}
+\section{Asteroseismic fitting}
 \label{fitting}
@@
 $M_*$ is the stellar mass.
-
-\input{gd358fit.tex} % label is gd358freq
 
@@
 
-\begin{deluxetable}{rrrrr}
+\begin{deluxetable}{llrrr}
 \tablecolumns{5}
@@
 \startdata
-%\input{journaldata.tex}
+\input{journaldata.tex}
 \enddata
@@
 
-%\input{1982freq.tex}
+\input{1982freq.tex}
 \clearpage
-%\input{2011freq.tex}
+\input{2011freq.tex}
 \clearpage
+\input{gd358fit.tex} % label is gd358freq
 \clearpage

### 2016-02-13 msnew.tex
smallfix
Updated some figures. Checked all references and other formatting issues. Some revisions to text all over. New discussion and conclusion section.

@@
 \newcommand{\logg}{$\log$g }
-\newcommand{\kic}{kic}
-\newcommand{\kicnsp}{kic }
+\newcommand{\kic}{KIC }
+\newcommand{\kicnsp}{KIC}
 \newcommand{\sigrms}{$\sigma_{\rm RMS}$}
@@
 \usepackage{graphicx}
-%\usepackage{array} %Don't activate doesn't play nice with deluxe tables!!!
+%\usepackage{array} %Don't activate - doesn't play nice with deluxe tables!!!
 \usepackage{epsfig}
@@
 \section{Astrophysical Context}
+\label{intro}
 White dwarfs are the end product of evolution for around 98\% of the stars in our Galaxy. 
@@
 frequency structure.  Models involving magnetic fields and oblique rotation have been 
-proposed to explain that structure \citep{Montgomery10}. Of importance for
-this work is the fact that the spacing of the multiplets is consistent with theoretical 
-predictions for a series of $\ell=1$ modes \citep{Provencal09}.
-
-Paradoxally, among the DBVs that have enough detected periods to be fitted 
-asteroseismically, GD358 is the only one that has not been analyzed using the complex 
-C/O profiles adapted and parameterized from stellar evolution calculations
-([e.g.][]\citet{Salaris97,Althaus05}). The most recent fits of GD358 \citep{Metcalfe03c} were 
-performed using 11 observed modes and simple models where the oxygen abundance 
-drops linearly from its central value to zero.
+proposed to explain that structure \citep{Montgomery10}.
 
@@
 
-We present a new detailed asteroseismic analysis of GD358, taking advantage of 
+Paradoxally, among the DBVs that have enough detected periods to be fitted 
+asteroseismically, GD358 is the only one that has not been analyzed using the complex 
+C/O profiles adapted and parameterized from stellar evolution calculations
+(e.g. {}\citet{Salaris97,Althaus05}). The most recent fits of GD358 \citep{Metcalfe03c} were 
+performed using 11 observed modes and simple models where the oxygen abundance 
+drops linearly from its central value to zero. We present a new detailed asteroseismic analysis of GD358, taking advantage of 
 its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
-define the limits of high precision white dwarf asteroseismology.  Our goals are two-fold.  
-First, we will incorporate advanced asteroseismic models to explore parameter space 
-\citep{BischoffKim14}. For example, the even period spacing observed in GD358's 
-pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
-magnitude of the spacing is expected to be related to how compressible the stellar 
-interior is. The compressibility of the interior should be inversely proportional to the 
-effective temperature. A hotter object would be less compact. On the other hand, a more 
-massive model will have a higher density and be less compressible. These properties lead 
-to distinguishable features of the models in the mass versus effective temperature 
-parameter plane. We can explore such features with GD358 because we have a long, 
-confirmed, single $\ell$ sequence of modes of higher radial order.
+define the limits of high precision white dwarf asteroseismology.
 
-Secondly, the present analysis allows us to place GD358 in the context of stellar evolution. 
+The present analysis allows us to place GD358 in the context of stellar evolution. 
 According to the models, the precursors of DBs emerge from the born-again phase with 
@@
 we can use to check this theory. The other three DBVs 
-(\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture consistent with 
+(\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture qualitatively consistent with 
 the diffusion calculations, with the hotter best fit models having thinner pure helium 
-layers. With GD358, we seek to confirm this trend qualitatively.
+layers. With GD358, we seek to confirm this trend.
 
@@
 In Section \ref{freq}, we establish the framework for frequency identification, and present the 
-list of frequencies used for the asteroseismic investigation.  Section \ref{fitting} outlines the 
-asteroseismic investigation, and .....
+list of frequencies used for the asteroseismic investigation.
+We perform further analysis of the observed frequencies in Section \ref{analysis}, and motivate the $\ell$ and $m$ identification of the modes.
+We present the asteroseismic fitting of GD358's pulsation spectrum in section \ref{fitting}, present the results in section \ref{results} and discuss our results in section \ref{discussion}.
 
@@
 New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
-2007-2015 (Table \ref{journal}. Each season of observations was obtained as part of 
+2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
 multisite WET campaigns.
@@
 with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
-representation of the fractional intensity of modulation (1 mmi $\approx$1 mmag). We present
+representation of the fractional intensity of modulation (1 mmi $\approx$ 1 mmag). We present
 our Fourier transforms (FTs) in units of modulation amplitude 
-($1\sim mma=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1\sim ppt$).
+($1 {\rm mma}=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1 {\rm ppt}$).
 
-The final reduction step is to combine the individual light curves (Figure \ref{tersk}) to produce 
+The final reduction step is to combine the individual light curves (one example shown in Fig. \ref{tersk}) to produce 
 complete light curves for GD358 for each observing season. We assume GD358 oscillates about 
@@
 \caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
-The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
+The frequency range of the observed series of $\ell=1$ modes discussed in section \ref{analysis} 
 is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
-frequencies discussed in Section \ref{analysis} (right arrow, blue). 
+frequencies discussed in section \ref{analysis} (right arrow, blue). 
 (A color version of this figure is available in the online journal.)
@@
 as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
-archival data is presented in Figure 3 of \citet{Provencal09}. To confirm our uncertainty 
+archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
 estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
@@
 different subsets of its available pulsations at different times. While this is a common phenomenon
-seen in white dwarf pulsators, the selection mechanism remains mysterious. The best way to 
+seen in white dwarf pulsators, the selection mechanism remains unknown. The best way to 
 determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
@@
 
-Figure~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
+Fig.~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
 available data. The features of asteroseismic importance are the localized bands between 900 and 2400
@@
 
-Figure \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
+Fig. \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
 \citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) KIC4552982, 
@@
 We measured the width of each of GD358's band. We define ''width'' as the difference between the 
-lowest and highest frequency detected in each band. Figure \ref{thick} presents the results. 
+lowest and highest frequency detected in each band. Fig. \ref{thick} presents the results. 
 The widths of GD358's bands are commensurate with those found in KIC4552982.  We also find a general 
 increase in width with decreasing frequency (increasing period), until we reach 
-the mode at 1238\muHz\ (807 s). This band has a width at least twice as wide as any other.  What 
+the mode at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.  What 
 is different about this mode???
@@
 \subsection{Mode Identification}
-
-GD358 is extensively studied \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}.  Our current 
-work has produced a well defined sequence of modes. The previous identification of these modes as 
+Our current work has produced a well defined sequence of modes, adding to previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous identification of these modes as 
 a series of $l$=1 radial overtones is based mostly on the pulsation frequency distribution 
 and limited spectroscopic analysis \citep{Kotak02, Castanheira05}. It is important to further 
-investigate these identifications as we initiate an indepth asteroseismic investigations.
+investigate these identifications as we initiate an indepth asteroseismic investigation.
 
@@
 
-Figure~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
-frequency as detected in 2014.
+Fig.~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
+frequency as detected in 2014. The mode is clearly identified as an $\ell=1$, $m=1$ mode.
 
@@
 Add table with all l,m ids
+%\label{tl}
+%isnt' that same as table \ref{gd}?
 
@@
 with numerous weighting techniques, and determined there is no significant difference in our solutions.  
-Our final frequency identification for each band is given in Table~\ref{tl}.
+Our final frequency identification for each band is given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.
 
@@
 
-\subsection{Initial grid search}
+\subsection{Initial Grid Search}
 \label{grids}
@@
 the mass and four structure parameters. There are two parameters associated with the shapes 
-of the oxygen (and carbon) core composition profiles: the central oxygen abundance ($X_o$) and 
-the edge of the homogeneous carbon and oxygen core ($q_{\rm fm}$, as a fraction of stellar mass. 
-For envelope structure, $M_{\rm env}$ marks the location of the base of the helium layer 
-and $M_{\rm He}$ the location where the helium abundance rises to $1$ (see Figure \ref{ffit1}). 
-$M_{\rm env}$ and $M_{\rm He}$ are mass coordinates, defined as e.g. 
-$M_{\rm env} = -\log(1 - M(r)/M_*)$, where $M(r)$ is the mass enclosed in radius r and 
-$M_*$ is the stellar mass.
+of the oxygen (and carbon) core composition profiles: the central oxygen abundance (\xo) and 
+the edge of the homogeneous carbon and oxygen core (\qfm, as a fraction of stellar mass. 
+For envelope structure, \menv marks the location of the base of the helium layer 
+and \mhe the location where the helium abundance rises to $1$ (see Fig. \ref{ffit1}). 
+\menv and \mhe are mass coordinates, defined as e.g. $M_{\rm env} = -\log(1 - M(r)/M_*)$, 
+where $M(r)$ is the mass enclosed in radius r and $M_*$ is the stellar mass.
+
+\begin{figure}
+%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
+%  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
+\plotone{ffit1.eps}
+\caption{
+{\em Upper panel:} Chemical composition profiles of the best fit model.
+The center of the model is to the left and the surface to the right.
+$q=2$ corresponds to $M_r = 0.99 \: M_*$.
+The vertical axis shows fractional abundances.
+{\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). \label{ffit1}
+}
+\end{figure}
 
 We started with a master grid (table \ref{fitt1}) chosen so that it covered all relevant 
-area of parameter space and had sufficient resolution, based on previous experience 
-\citep{Bischoff-Kim11a,Bischoff-Kim14} to find any region of local minimum in the fitness parameter, 
-but was small enough to be computationally manageable. The master grid involved the computation 
+area of parameter space and had sufficient resolution to find any region of local minimum in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}.
+We used the minimum resolution that was computationally manageable.
+The master grid involved the computation
 of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
-modes. A fitness map of this initial fit are shown in the left panel of figure \ref{ffit2}, and the parameters of the best fit model are listed in table \ref{fitt1}.
+modes. A fitness map of this initial fit are shown in the left panel of Fig. \ref{ffit2}, and the parameters of the best fit model are listed in table \ref{fitt1}.
 
-\subsection{Asymptotic period spacing}
+\subsection{Asymptotic Period Spacing}
 \label{periodspacing}
@@
 Before we refine the period-by-period fitting optimization, it is worth stepping back and consider 
-what we can learn from the average period spacing of GD358. The average period spacing provides a 
-useful asteroseismic measure of the mass and temperature of the star, independent of the details of 
+what we can learn from the average period spacing of GD358. The average period spacing provides an asteroseismic measure of the mass and temperature of the star, independent of the details of 
 internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
@@
 fitting of white dwarfs and also sdB stars as a ubiquitous diagonal trend in contour maps of the quality 
-of the fits in the mass-effective temparature plane \citep[e.g][]{Bischoff-Kim14,Castanheira09,Charpinet08}. 
+of the fits in the mass-effective temperature plane \citep[e.g][]{Bischoff-Kim14,Castanheira09,Charpinet08}. 
 One requirement for the periods of the model to match the observed periods is that the average period spacing 
@@
 
-We can use the sequence of 13 consecutive $\ell=1$ modes we have with GD 358 to calibrate our models. 
-Using the $ell=1$ sequence of modes, we compute an average period spacing of 39.08 seconds. We call 
+We can use the sequence of 13 consecutive $\ell=1$ modes found in GD358's pulsation spectrum to calibrate our models. 
+Using the $\ell=1$ sequence of modes, we compute an average period spacing of 39.08 seconds. We call 
 this $\Delta P_{\rm obs}$. For each model in the master grid, we compute an asymptotic period spacing 
-($\Delta P_{\rm calc}$). This asymptotic period spacing is calculated by first discarding the first 
-10 modes. The exact value of 10 is somewhat arbitrary, but it is chosen so that the modes we use in 
+($\Delta P_{\rm calc}$).
+This asymptotic period spacing is calculated by first discarding the 10 lowest $k$ modes.
+The exact value of 10 is somewhat arbitrary, but it is chosen so that the modes we use in
 our computation are indeed in the asymptotic limit. The higher $k$ modes show weaker trapping than the 
 lower $k$ modes. We then fit a line through the set ($k_i$,$P_i$). The slope gives us the asymptotic 
-period spacing in the model. We also calculate the residuals of the fits and as an additional check, 
-discard the models that have residuals above a certain limit. The limit is chosen by checking the procedure 
+period spacing in the model. We also calculate the residuals of the fits and discard the models that have residuals above a certain limit. The limit is chosen by checking the procedure 
 by eye on a few models.
@@
 We show a contour map of the location of the models that best match the average period spacing of 
-39.08 seconds in Fig. \ref{ffit1}, right panel. We place it side by side with a contour map showing 
+39.08 seconds in Fig. \ref{ffit2}, right panel. We place it side by side with a contour map showing 
 the location of the best fit model in the same region of parameter space, based on the master grid 
@@
 Note that the period spacing is a much weaker constraint than the individual period fit. 
-If one takes 4 seconds as an upper limit for fitness, that includes a single point in the 
+If one takes 5.0 seconds as an upper limit for goodness of fit, that includes 9 points in the 
 period-by-period fit plot (left panel in Fig \ref{ffit2}), but the entire parameter plane 
@@
 a higher resolution grid that fall within the region defined by the two diagonal lines shown 
-in the right panel of figure \ref{ffit2} (covering the effective temperature range 25,000~K-27,500~K, then performing a period-by-period fit using 
+in the right panel of Fig. \ref{ffit2} (covering the effective temperature range 25,000~K-27,500~K), then performing a period-by-period fit using 
 equation \ref{fiteq1}.
 
-%If we now look for the models that have $\Delta P_{\rm calc} = \Delta P_{\rm obs} = 39.08$ s 
-%and plot their mass and effective temperature, we do recover the expected diagonal trend 
-%(Fig \ref{ffit}). We can use the asymptotic period spacing to calibrate our models. Before 
-%we seek the detailed chemical make-up by performing period-by-period matching, we can 
-%test whether the bulk properties of our models are consistent with our observations of the 
-%stars. With spectroscopy, we can obtain a measurement of the effective temperature, and 
-%with the addition of a mass-radius relation, the star mass. For GD 358, we use results 
-%quoted in XXX and XXX. Both (all X) values are included on Fig. \ref{f3}. We see that our 
-%trend of best match between the calculated and the observed average period spacings goes 
-%right through the data points. GD 358 is the first DBV for which we are able perform this 
-%test. Our models have bulk properties that appear consistent with at least one real star. 
-%We confidently move on to our period-by-period fitting.
-
-\subsection{Determining the best grid resolution for refined fits}
+\subsection{Optimal Grid Resolution}
 \label{refinedfits}
@@
 We allowed the effective temperature to vary through the entire range 
-considered for the master grid (table \ref{fitt1}). One can see that the 
-fits are generally poor, though they do seem to settle to a minimum in a 
-smooth way. Except for the striking anomaly at 26,600~K. Upon further 
+considered for the master grid. The fits seem to settle to a minimum in a 
+smooth way, except for the striking anomaly at 26,600~K. Upon further 
 investigation, we discovered that anomaly to be due to a single period in 
-the pulsation spectrum: the 968~s mode. In the model, that mode appears 
+the pulsation spectrum: the 968~s mode. In the models, that mode appears 
 highly sensitive to some parameters, and in a non-continuous way.
@@
 we ran systematic scans, computing models with 5 parameter fixed and allowing 
-the 6th parameter to vary in very fine steps. We went all the way down in 
-step sizes to $\Delta {\rm T_{eff}}=1$~K, $\Delta M_*=0.1 M_\odot$, 
-$\Delta M_{\rm env}= \Delta M_{\rm He}=1$, $\Delta X_o=1$, and $\Delta q_{\rm fm}=0.1$. 
+the 6th parameter to vary in very fine steps. We went down in 
+step sizes to $\Delta {\rm T_{eff}}=1$~K, $\Delta M_*=0.0001 M_\odot$, 
+$\Delta M_{\rm env}= \Delta M_{\rm He}=0.01$ dex, $\Delta X_o=0.01$, and $\Delta q_{\rm fm}=0.001$. 
 Results for 4 different parameters are shown in Fig \ref{ffit4}. The figure 
@@
 similar to the 968~s mode, in different regions of parameter space. For instance, 
-the jumps in $\sigma_{\rm RMS}$ for $q_{\rm fm}$ between 0.3 and 0.4 are due 
+the jumps in \sigrms\ for \qfm\ between 0.3 and 0.4 are due 
 to sudden changes in the 854.5 and 902.5~s modes.
@@
 of missing a minimum. We settled on optimal step sizes of 
-$\Delta {\rm T_{eff}}=20$, $\Delta M_*=0.2$, $\Delta M_{\rm He}=20$, 
-$\Delta X_o=20$, and $\Delta q_{\rm fm}=1$ for our refined grid. To offset 
+$\Delta {\rm T_{eff}}=20$, $\Delta M_*=0.0002$, $\Delta M_{\rm He}=0.2$, 
+$\Delta X_o=0.2$, and $\Delta q_{\rm fm}=0.01$ for our refined grid. To offset 
 the computational cost, we fixed $M_{\rm env}$ to a canonical value of 
@@
 \begin{figure}
-\epsscale{0.7}
+\epsscale{0.9}
 \plotone{ffit4.eps}
@@
 \label{ffit4}
-Dependence of the fitness parameter on different parameters. The 5 parameters not 
-shown on the horizontal axis in each plot are held to fixed values corresponding 
-to the best fit model. \label{ffit4}
+Dependence of the fitness parameter on different parameters.
+The 5 parameters other than the one shown on the horizontal axis in each plot are held to fixed values corresponding to the best fit model (table \ref{ffit1}).
 }
+
 \end{figure}
 
-\section{Results of the period fitting}
+\section{Results of the Period Fitting}
+\label{results}
 
 The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in table \ref{gd}.
-The goodness of fit of the model is $sig_RMS = 4.22 s$.
+The goodness of fit of the model is \sigrms$=4.22$~s.
 In Fig.
@@
 
-\begin{figure}
-%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
-%  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
-\plotone{ffit1.eps}
-\caption{
-{\em Upper panel:} Chemical composition profiles of the best fit model.
-The center of the model is to the left and the surface to the right.
-$q=2$ corresponds to $M_r = 0.99 \: M_*$.
-The vertical axis shows fractional abundances.
-{\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). \label{ffit1}
-}
-\end{figure}
-
-\subsection{Validation of the fitting method}
+\subsection{Validation of the Fitting Method}
 
@@
 We performed a simple test to validate our fitting method, which consisted of using the exact same procedure to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that were very close to the best fit model.
-We used the period list for a model with parameters ${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, fixing $M_{\rm env}$ to -2.80, including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
+We used the period list for a model with parameters ${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, fixing $M_{\rm env}$ to -2.80, and including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
 
@@
 Then we refined our fits, using the grids described at the end of section \ref{periodspacing}.
-We are able to recover the best fit parameters adequately, with the top 10 best fit models having parameters ${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 10 fits, and $q_{\rm fm}=0.175 \pm 0.5$.
+We are able to recover the best fit parameters adequately, with the top 10 best fit models having parameters ${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_\odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 10 fits, and $q_{\rm fm}=0.175 \pm 0.5$.
 The top 10 best fits have \sigrms $\sim$ 0.5~s.
@@
 
+We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 24000~K \citep{Koester2013} by more than one sigma (the mass matches the spectrosocopy).
+For reasons discussed in section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting.
+As we can see from Fig.
+\ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at lower effective temperature.
+Structure parameters, especially the location of chemical transitions (with the exception of \menv\ in the case of GD358) are more tightly constrained.
+
 In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness number.
@@
 Any search algorithm that uses a small enough mesh should be able to find the minimum.
-This phenomenon likely became apparent while fitting GD358 because with that star, we are fitting a long consecutive sequence of modes of the same ell.
+This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
 
-We have performed and published a preliminary fit of the star (Hawaii proceedings), where we found a temperature of 23,600 K, a mass of 0.605 $M_\odot$, \menv = -2.40, \mhe = -5.20, a central oxygen abundance of 0.99, and \qfm = 0.50.
+In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
+We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
+Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058).
+It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
+Pinning down the proper effective temperature of each star is challenging.
+To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically.
+At best we can contrast blue edge versus red edge objects.
+
+Numerical experiments of the type presented in section \ref{refinedfits} \citep{Bischoff-Kim15} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur.
+Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.
+We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs.
+It is unclear how much of an effect on structure parameters a change in parameterization would have.
+
+%We have performed and published a preliminary fit of the star (Hawaii proceedings), where we found a temperature of 23,600 K, a mass of 0.605 $M_\odot$, \menv = -2.40, \mhe = -5.20, a central oxygen abundance of 0.99, and \qfm = 0.50.
 In the preliminary fits, the period list was not finalized and we did not include the 1065.260 s mode, because it was difficult to fit and we did not have a positive ell identification for the mode.
@@
 We emphasize again that in the final stages of our fitting for this work, we fixed the envelope mass to -2.80.
-
-In section \ref{periodspacing}, we discussed the degeneracy in the determination of the mass and effective temperature parameters.
+%
+%In section \ref{periodspacing}, we discussed the degeneracy in the determination of the mass and effective temperature parameters.
 That degeneracy means that a unique determination of effective temperature and mass is not always possible.
@@
 We should also keep in miind that the period lists used in the fits were close but not identical.
-
-Lessons learned: how fine a grid must be. CAUTION with pipeline fitting. we learn that one must 
-exert extreme caution in any automated pipeline-type fitting of white dwarf stars.
-Asymptotic theory \\
-We recover the trend in mass/teff plane \\
-We confirm the weak dependence on 4 interior parameters. \\
-We calibrated our models.
 
@@
 \tablewidth{0pc}
-\tablecaption{}
+\tablecaption{\label{journal}}
 \tablehead{
@@
 \colhead{} & \colhead{} & \colhead{} & \colhead{} & \colhead{(hrs)}
-\label{journal}}
+}
 \startdata
@@
 
-\input{1982freq.tex}
+\input{1982freq.tex} % \label{freq1}
 \clearpage
-\input{2011freq.tex}
+\input{2011freq.tex} %\label{freq2}
 \clearpage
-\input{gd358fit.tex} % label is gd358freq
+\input{gd358fit.tex} % \label{gd}
 \clearpage
-\input{fitt1} % label is fitt1
+\input{fitt1} % \label{fitt1}
 \clearpage

### 2016-02-15 msnew.tex
Partial abstract added

@@
 \begin{abstract}
-We report on ......
+We report on the analysis of XXXX numbers of hours of data collected on the pulsating helium atmosphere white dwarf star, GD358.
+From this data set added to archival data, we extract 15 frequencies, adding 4 modes to the 11 modes known previously.
+We present evidence that the 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in $k$.
+We use models that include parameterized, complex carbon and oxygen core composition profiles to fit the periods.
 \end{abstract}
@@
 Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058).
-It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
+It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
 Pinning down the proper effective temperature of each star is challenging.
@@
 
-Numerical experiments of the type presented in section \ref{refinedfits} \citep{Bischoff-Kim15} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur.
+Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur \citep{Bischoff-Kim15}.
 Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.

### 2016-02-18 msnew.tex
msnew.tex

@@
 \newcommand{\teff}{$\rm T_{eff}$}
-\newcommand{\logg}{$\log$g }
+\newcommand{\logg}{$\log$\ g }
 \newcommand{\kic}{KIC }
@@
 \begin{abstract}
-We report on the analysis of XXXX numbers of hours of data collected on the pulsating helium atmosphere white dwarf star, GD358.
-From this data set added to archival data, we extract 15 frequencies, adding 4 modes to the 11 modes known previously.
-We present evidence that the 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in $k$.
-We use models that include parameterized, complex carbon and oxygen core composition profiles to fit the periods.
+We report on the analysis 33 years (1982-2015) of photometric observations of the pulsating
+helium atmosphere white dwarf GD358.  The data set includes 1105.1 hours of new observations
+from 2007-2015. From this data set, we extract 15 frequencies representing a sequence 
+of radial pulsation modes, adding 4 modes to the 11 modes known previously. We present evidence 
+that these 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in radial overtone
+$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
+core composition profiles to fit the periods.Our results indicate.....
+
 \end{abstract}
@@
 studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
-instability strip, with \teff of 24000~K and \logg of 7.8 \citep{Koester2013}. GD358's 
-pulsation spectrum contains a series of independent modes, many with complex 
-frequency structure.  Models involving magnetic fields and oblique rotation have been 
-proposed to explain that structure \citep{Montgomery10}.
+instability strip, with a spectroscopic temperature of \teff\ $=24000\pm500$ ~K and \logg\ $=7.8$ 
+\citep{Koester2013}. GD358's pulsation spectrum contains a series of independent 
+modes, many with complex frequency structure.  Models involving magnetic fields and oblique rotation 
+have been proposed to explain that structure \citep{Montgomery10}.
 
-Pulsating white dwarfs do not pulsate in all their available modes at all times.  
-We have maintained an active observing program of this complex star in an effort 
-to identify additional frequencies. These new observations have identified additional 
+Since the 2006 Whole Earth Telescope (WET) run reported in \citet{Provencal09}, 
+we have maintained an active observing program of GD358 in an effort to identify additional
+frequencies in this complex star. These new observations have identified additional 
 periods in GD358's pulsation spectrum, bringing the total known modes to 15. Thirteen of 
 these modes belong to a consecutive $\ell=1$ sequence, the longest sequence observed 
-in a DBV. This sequence is critical to constrain the asteroseismic fits and better define the
-limitations of high precision white dwarf asteroseismology.
+in a DBV.
 
-Paradoxally, among the DBVs that have enough detected periods to be fitted 
+Paradoxally, among the DBVs with enough detected periods to be fitted 
 asteroseismically, GD358 is the only one that has not been analyzed using the complex 
@@
 
-The final reduction step is to combine the individual light curves (one example shown in Fig. \ref{tersk}) to produce 
+The final reduction step is to combine the individual light curves (an example is shown in Fig. \ref{tersk}) to produce 
 complete light curves for GD358 for each observing season. We assume GD358 oscillates about 
@@
 the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
-are combination frequencies \citep{Provencal09}.  Fig.~\ref{noise} displays the average noise 
+are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
 as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
@@
 
-Fig.~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
-available data. The features of asteroseismic importance are the localized bands between 900 and 2400
+Fig.~\ref{schematic} presents a schematic representation of GD358's 
+independent frequencies detected between 1982 and 2015.  
+The features of asteroseismic importance are the localized bands between 900 and 2400
 \muHz\ (1100 and 400 s). We interpret each band to represent a single radial overtone. The bands
@@
 from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
-distributions of the lower frequency (longer period) bands. The lower frequency band widths are 
+distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
 most likely the result of amplitude and/or frequency modulation that obscures any underlying 
@@
 increase in width with decreasing frequency (increasing period), until we reach 
-the mode at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.  What 
-is different about this mode???
+the mode at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.
 
+A second interesting pattern is given by the distribution of amplitudes for the modes.  In particular, the 
+two modes at 2007.6 and 1857.7 \muHz\ have never been observed at amplitudes above 4 mma.  Interestingly, the 
+mode at 1741.5 \muHz\ was not observed at large amplitude prior to 2006.  This ``zone of avoidance'' is telling 
+us something about the structure of the star. Lower frequency modes preferentially sample the outer layers of 
+the star.  
 \begin{figure}
@@
 
-\subsection{Mode Identification}
+\subsection{Mode Identification}\label{mode}
 Our current work has produced a well defined sequence of modes, adding to previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous identification of these modes as 
@@
 \label{ffit4}
-Dependence of the fitness parameter on different parameters.
-The 5 parameters other than the one shown on the horizontal axis in each plot are held to fixed values corresponding to the best fit model (table \ref{ffit1}).
+Dependence of the fitness parameter on different parameters. The 5 parameters other than the one shown 
+on the horizontal axis in each plot are held to fixed values corresponding to the best fit model (table \ref{ffit1}).
 }
@@
 
-The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in table \ref{gd}.
-The goodness of fit of the model is \sigrms$=4.22$~s.
-In Fig.
-\ref{ffit1}, we show the interior structure of the best fit model, with the corresponding \bvf frequency profile.
+The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in 
+Table \ref{gd}. The goodness of fit of the model is \sigrms$=4.22$~s. In Fig. \ref{ffit1}, we show the interior structure of 
+the best fit model, with the corresponding \bvf frequency profile.
 
@@
 
-With what we have discovered in section \ref{refinedfits}, it is only natural to be concerned about whether we have truly found a best fit.
-We performed a simple test to validate our fitting method, which consisted of using the exact same procedure to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that were very close to the best fit model.
-We used the period list for a model with parameters ${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, fixing $M_{\rm env}$ to -2.80, and including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
+With what we have discovered in section \ref{refinedfits}, it is only natural to be concerned about whether we have truly 
+found a best fit. We performed a simple test to validate our fitting method, which consisted of using the exact same procedure 
+to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that 
+were very close to the best fit model. We used the period list for a model with parameters 
+${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, 
+fixing $M_{\rm env}$ to -2.80, and including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
 
-We first performed a fitting of the periods using the master (coarse) grid described in section \ref{grids}.
-This placed the best fit model in the appropriate region of parameter space.
-Then we refined our fits, using the grids described at the end of section \ref{periodspacing}.
-We are able to recover the best fit parameters adequately, with the top 10 best fit models having parameters ${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_\odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 10 fits, and $q_{\rm fm}=0.175 \pm 0.5$.
-The top 10 best fits have \sigrms $\sim$ 0.5~s.
-We remind the reader that the step sizes in the second phase of the fitting are 20~K for ${\rm T_{eff}}$, 0.2 for $M_{\rm He}$, 0.2 for $X_o$, and 0.01 for $q_{\rm fm}$.
+We first performed a fitting of the periods using the master (coarse) grid described in section \ref{grids}. This 
+placed the best fit model in the appropriate region of parameter space. Then we refined our fits, using the grids 
+described at the end of section \ref{periodspacing}. We are able to recover the best fit parameters adequately, with 
+the top 10 best fit models having parameters 
+${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_\odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 
+10 fits, and $q_{\rm fm}=0.175 \pm 0.5$. The top 10 best fits have \sigrms $\sim$ 0.5~s. We remind the reader that 
+the step sizes in the second phase of the fitting are 20~K for ${\rm T_{eff}}$, 0.2 for $M_{\rm He}$, 0.2 for $X_o$, 
+and 0.01 for $q_{\rm fm}$.
 
@@
 
-We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 24000~K \citep{Koester2013} by more than one sigma (the mass matches the spectrosocopy).
-For reasons discussed in section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting.
-As we can see from Fig.
-\ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at lower effective temperature.
-Structure parameters, especially the location of chemical transitions (with the exception of \menv\ in the case of GD358) are more tightly constrained.
+We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 
+24000~K \citep{Koester2013} by more than one sigma (the mass matches the spectrosocopy). For reasons discussed in 
+section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the 
+blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting. As we can 
+see from Fig. \ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at 
+lower effective temperature. Structure parameters, especially the location of chemical transitions 
+(with the exception of \menv\ in the case of GD358) are more tightly constrained.
 
-In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness number.
-This is due to the fact that some periods can change values drastically for a small change in a given parameter.
-The phenomenon is only semi-chaotic, as the period will oscillate between two values.
-This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
-Any search algorithm that uses a small enough mesh should be able to find the minimum.
-This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
+In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of 
+parameters able to yield very different fitness number. This is due to the fact that some periods can change values 
+drastically for a small change in a given parameter. The phenomenon is only semi-chaotic, as the period will oscillate 
+between two values. This is good news, because there remains a well defined minimum in parameter space, even if it is a 
+double valued minimum. Any search algorithm that uses a small enough mesh should be able to find the minimum. This 
+phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long 
+consecutive sequence of modes of the same $\ell$ with high resolution grids.
 
-In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
-We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
-Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058).
-It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
-Pinning down the proper effective temperature of each star is challenging.
-To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically.
-At best we can contrast blue edge versus red edge objects.
+In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so 
+that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, 
+EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of 
+asteroseismic fitting that used a consistent set of models. Unfortunately, GD358 does not fit neatly into the 
+trend (neither does EC20058). It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have 
+thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for 
+GD358 and $-5.94$ for CBS114. Pinning down the proper effective temperature of each star is challenging. To be 
+fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly 
+constrained asteroseimically. At best we can contrast blue edge versus red edge objects.
 
-Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur \citep{Bischoff-Kim15}.
-Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.
-We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs.
-It is unclear how much of an effect on structure parameters a change in parameterization would have.
+Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with 
+the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition 
+zones occur \citep{Bischoff-Kim15}. Modern asteroseismic fitting vary parameters attached to the shape of 
+transition zones \citep{Giammichele15}. We refrained from doing this in the present study because we wanted 
+to compare our results with previous studies of DBVs. It is unclear how much of an effect on structure 
+parameters a change in parameterization would have.
 

### 2016-03-03 msnew.tex
Some updates to manuscript

@@
 \begin{abstract}
-We report on the analysis 33 years (1982-2015) of photometric observations of the pulsating
-helium atmosphere white dwarf GD358.  The data set includes 1105.1 hours of new observations
-from 2007-2015. From this data set, we extract 15 frequencies representing a sequence 
-of radial pulsation modes, adding 4 modes to the 11 modes known previously. We present evidence 
-that these 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in radial overtone
+We report on the analysis of 33 years of photometric observations of the pulsating
+helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
+and 1105.1 hours of new observations from 2007-2015. From this data set, we extract 15 frequencies 
+representing g-mode pulsation modes, adding 4 modes to the 11 modes 
+known previously. We present evidence that these 15 modes are $\ell=1$ modes, 13 of which belong to 
+a consecutive sequence in radial overtone
 $k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
-core composition profiles to fit the periods.Our results indicate.....
+core composition profiles to fit the periods.
+Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex.
+The surface gravity translates to a mass range of 0.455 to 0.540 \msun.
+Our best fit model is slightly more massive and much hotter (by 2,000~K) than the most recent spectroscopy indicates.
+We find a pure helium layer mass of $10^{-5.40}$, consistent with a red edge object when compared with other DBVs analyzed using the same models.
 
@@
 in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
-are then supposed to return to the white dwarf cooling track as PG 1159 stars, which are 
+then return to the white dwarf cooling track as PG 1159 stars, which are 
 widely believed to be the precursors of most DB white dwarfs. DBs are found to pulsate at 
@@
 performed using 11 observed modes and simple models where the oxygen abundance 
-drops linearly from its central value to zero. We present a new detailed asteroseismic analysis of GD358, taking advantage of 
-its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
-define the limits of high precision white dwarf asteroseismology.
+drops linearly from its central value to zero. We present here a new detailed asteroseismic analysis 
+of GD358, taking advantage of its long sequence of $\ell=1$ modes to better constrain 
+the asteroseismic fits and define the limits of high precision white dwarf asteroseismology.
 
-The present analysis allows us to place GD358 in the context of stellar evolution. 
+The present analysis also allows us to place GD358 in the context of stellar evolution. 
 According to the models, the precursors of DBs emerge from the born-again phase with 
@@
 2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
-multisite WET campaigns.
+multisite WET campaigns \citep{wet90}.
 
-Standard WET procedure calls for observers to transfer raw images and 
-calibration files to WET headquarters for analysis at the end of each local night. CCD 
-data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
+Data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
 were obtained with different CCD photometers, each with distinct effective bandpasses. 
@@
 our Fourier transforms (FTs) in units of modulation amplitude 
-($1 {\rm mma}=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1 {\rm ppt}$).
+($1\ {\rm mma}=1 \times 10^{-3}\ {\rm ma} = 0.1 \% = 1\ {\rm ppt}$).
 
-The final reduction step is to combine the individual light curves (an example is shown in Fig. \ref{tersk}) to produce 
-complete light curves for GD358 for each observing season. We assume GD358 oscillates about 
-a mean light level. This assumption allows us to carefully assess overlapping segments from 
-different telescopes and identify and correct any vertical offsets. As discussed in detail 
-in \citet{Provencal09}, we find no significant differences between the noise levels of 
-amplitude spectra using: 1) the combination of all light curves including overlapping 
+The final reduction step is to combine the individual light curves 
+(an example is shown in Fig. \ref{tersk}) to produce complete light curves for GD358 for each 
+observing season. We assume GD358 oscillates about a mean light level. This assumption 
+allows us to carefully assess overlapping segments from different telescopes and identify 
+and correct any vertical offsets. As discussed in detail in \citet{Provencal09}, we find 
+no significant differences between the noise levels of amplitude spectra using: 
+1) the combination of all light curves including overlapping 
 segments from different telescopes, 2) the combination of light curves where we retain 
@@
 \plotone{terskol}
-\caption{Light curve of GD358 obtained with the Peak Terskol 2.0m.  Each point corresponds 
+\caption{Light curve of GD358 obtained with the Peak Terskol 2.0 m telescope.  Each point corresponds 
 to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
+(A color version of this figure is available in the online journal.)
 \label{tersk}
@@
 
-The result is a series of new light curves for each observing season between 2007 and 2015. 
-2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 2010 201.3 hrs, 2011 
-401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. Our coverage is 
-not complete, and this incompleteness produces spectral leakage in the amplitude spectra. 
-To quantify this, we sampled single sinusoids using exactly the same times as the original 
-data for each season. The resulting amplitude spectrum, or ``spectral window'', is the 
-pattern produced in the FT by a single frequency. The FTs for 2010, 2011, and 2014 
-are given in Fig.~\ref{fts}.
+The complexities associated with GD358's pulsations (see Section \ref{freq}) led us to also 
+re-reduce all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
+insure continuity in methodology. The final result is a series of light curves 
+for each observing season between 1982 and 2015. 
+For the new observations, 2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 
+2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. 
+Our coverage is not complete, and this incompleteness produces spectral leakage in the 
+amplitude spectra. To quantify this, we sampled single sinusoids using exactly the 
+same times as the original data for each season. The resulting amplitude spectrum, 
+or ``spectral window'', is the pattern produced in the FT by a single frequency. 
+The FTs for 2010, 2011, and 2014 are given in Fig.~\ref{fts}.
 
@@
 \caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
-The frequency range of the observed series of $\ell=1$ modes discussed in section \ref{analysis} 
+The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
 is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
-frequencies discussed in section \ref{analysis} (right arrow, blue). 
+frequencies discussed in Section \ref{mode} (right arrow, blue). 
 (A color version of this figure is available in the online journal.)
@@
 amplitudes and small but not insignificant frequency variations on a variety of timescales 
-\citep{Provencal09}.  The amplitude and frequency variations evident in Fig.~\ref{fts} will 
-produce artifacts in FTs, greatly complicating any frequency analysis.  
-We reanalyzed all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
-as well as our new observations to insure continuity in methodology.  We use 
-{\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
-select statistically significant peaks in each FT.  As discussed in \citet{Provencal12}, 
-we adopt the criterion that a peak must have an amplitude at least four times greater than the 
-average noise level in the given frequency range. We define ``noise'' as the frequency-dependent 
-average amplitude after prewhitening by the dominant frequencies. This is a conservative estimate, 
+\citep{Provencal09, Kepler03}.  The amplitude and frequency variations evident in Fig.~\ref{fts} demonstrate that 
+it is not feasible to analyze the entire data set as one unit. To minimize the effects of the long term  
+amplitude and frequency variations, we analyze the light curves from each observing season individually.
+
+We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
+select statistically significant peaks in each FT. We adopt the criterion that a peak must have 
+an amplitude at least four times greater than the average noise level in the given frequency range 
+\citep{Provencal12}. We define ``noise'' as the frequency-dependent 
+average amplitude after removal of the dominant frequencies. This is a conservative estimate, 
 as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
@@
 
+Having established our baseline noise levels, we proceed to frequency selection and identification.
 Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
@@
 The features of asteroseismic importance are the localized bands between 900 and 2400
-\muHz\ (1100 and 400 s). We interpret each band to represent a single radial overtone. The bands
+\muHz\ (1100 and 400 s). We interpret the bands to represent a series of radial overtone $k$. The bands
 themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
@@
 distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
-most likely the result of amplitude and/or frequency modulation that obscures any underlying 
-signatures of rotational splitting.
+most likely the result of some process producing amplitude and/or frequency modulation that obscures 
+any underlying signatures of rotational splitting.
 
@@
  \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
- and 2360 \muHz\ ({\em{left}}). The 1300 \muHz\ band shows no multiplet structure, unlike the 2360 \muHz\
- band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
- $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
+ and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1300 \muHz\ band 
+ shows no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
+ structure. Assuming the triplet represents
+ $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the x scale for both axes.
  (A color version of this figure is available in the online journal.)
@@
 
-Fig. \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
-\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) KIC4552982, 
-in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
+Fig. \ref{schematic} also shows that the widths of the bands are not constant, but change 
+from band to band. \citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator 
+(DAV) KIC4552982, in which they identify 17 bands of pulsation frequencies. KIC4552982 is one of the 
+coolest ZZ Cetis known \citep{Tremblay2013}, and it follows the general pattern exhibited 
 by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
 lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
-different widths in frequency space, and that there may be astronomical significance to this. Although the 
-observational timebases and coverage are quite different (20 continuous months for KIC4552982 vs 30 
-incomplete years for GD358), our data presents the opportunity to investigate this for a DB pulsator.  
-We measured the width of each of GD358's band. We define ''width'' as the difference between the 
-lowest and highest frequency detected in each band. Fig. \ref{thick} presents the results. 
-The widths of GD358's bands are commensurate with those found in KIC4552982.  We also find a general 
-increase in width with decreasing frequency (increasing period), until we reach 
-the mode at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.
+different widths in frequency space, and that there may be astronomical significance to this. 
+Although the observational timebases and coverage are quite different (20 continuous months 
+for KIC4552982 vs 33 incomplete years for GD358), our data presents the opportunity to investigate this 
+for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
+more than 10 detections. We define ''width'' as the difference between the lowest and highest frequency 
+detected in each band. Fig. \ref{thick} presents the results. We find no correlation of width with number
+of detected peaks in each band. Interestingly, the widths of GD358's bands are commensurate with those 
+found in KIC4552982. We find a general increase in width with decreasing frequency (increasing period), 
+until we reach the band at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.
 
-A second interesting pattern is given by the distribution of amplitudes for the modes.  In particular, the 
-two modes at 2007.6 and 1857.7 \muHz\ have never been observed at amplitudes above 4 mma.  Interestingly, the 
-mode at 1741.5 \muHz\ was not observed at large amplitude prior to 2006.  This ``zone of avoidance'' is telling 
-us something about the structure of the star. Lower frequency modes preferentially sample the outer layers of 
-the star.  
+A second interesting behavior is given by the distribution of average amplitudes for the bands 
+(Fig~\ref{schematic}. In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
+at amplitudes above 4 mma. The band at 1369 \muHz\ is also only observed at lower amplitudes. Interestingly, 
+the band at 1741.5 \muHz\ was not observed at large amplitude prior to 2006, and it has remained at high 
+amplitude since that time.
+
+In broad brush strokes, the observed global pulsations involve the whole star, but each pulsation samples the star
+in slightly different ways.  For example, modes with lower frequencies (higher radial $k$ values) preferentially 
+sample the outer layers, while modes with higher frequencies (lower radial $k$ values) have outer turning points 
+that are farther from the surface, and so sample the deeper interior. It makes intuitive sense that lower 
+frequency modes would be affected by processes confined to the outer stellar atmosphere. We speculate that the 
+observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface
+magnetic field. Further investigation requires guidance from theory.
+
 \begin{figure}
@@
 \subsection{Mode Identification}\label{mode}
-Our current work has produced a well defined sequence of modes, adding to previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous identification of these modes as 
-a series of $l$=1 radial overtones is based mostly on the pulsation frequency distribution 
-and limited spectroscopic analysis \citep{Kotak02, Castanheira05}. It is important to further 
-investigate these identifications as we initiate an indepth asteroseismic investigation.
+Our current work has produced a well defined sequence of modes, adding to 
+previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous 
+identification of these modes as a series of $l$=1 radial overtones is based mostly on 
+the pulsation frequency distribution and limited spectroscopic analysis 
+\citep{Kotak02, Castanheira05}. It is important to further investigate these identifications 
+as we initiate an indepth asteroseismic investigation.
 
@@
 
-Fig.~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
-frequency as detected in 2014. The mode is clearly identified as an $\ell=1$, $m=1$ mode.
+As an example, Fig.~\ref{modeamps} shows the probability distribution of $\ell$ and $m$ 
+values for the 1735.96 \muHz\ frequency as detected in 2014. To produce the distribution, we ran
+the amplitude code \citep{Montgomery10} 1000 times, and selected the results having $Res_{rms}<9.5\times10^{-06}$, 
+where $Res_{rms}$ are the root-mean-squared residuals between predicted and observed amplitudes.  
+For our example, this mode is clearly preferred as an $\ell=1$, $m=1$ mode. We find similar results for all
+modes above 10 mma in the 1990, 1994, 2006, 2010, and 2014 observing seasons. Combining the results from the 
+combination frequencies with previous evidence, we are confident that the bands in Fig.~\ref{schematic} represent
+a series of $\ell=1$ modes.
 
@@
  \caption{Probability distribution (from 0 to 1) of $\ell$ and $m$ values for the 1735.96 variation detected in 
- 2014.  The solutions are from individual simulations with $Res_{rms}<9.5^{-06}$. The amplitudes of the 
- observed combination frequencies argue that this is $\ell=1$, $m$=1.  
+ 2014.  The distribution is produced from 1000 simulations, selecting with $Res_{rms}<9.5^{-06}$. 
+ The amplitudes of the observed combination frequencies argue that this is $\ell=1$, $m$=1.  
  \label{modeamps}
@@
 
-Add table with all l,m ids
-%\label{tl}
 %isnt' that same as table \ref{gd}?
 
-Finally, given the $l$=1 identification, but the lack of definite multiplet structure, the best way to 
-determine the l=0 component for each band is simply to average the frequencies in the bands.  We experimented
-with numerous weighting techniques, and determined there is no significant difference in our solutions.  
-Our final frequency identification for each band is given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.
+Finally, given the $l$=1 identification and the lack of definite multiplet structure for the higher 
+frequency modes, the best way to determine the central frequency for each band is simply to 
+average the detected frequencies in the bands.  We experimented with numerous weighting techniques, 
+and determined there is no significant difference in our solutions.  Our final frequencies for each band 
+are given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.
 
@@
 The basic method in our asteroseismic fitting consists of calculating grids of white dwarf models and 
-running a fitting subroutine to match the periods of the models ($\rm P_{calc}$) with the observed 
-periods and calculated residuals using the usual formula
+running a fitting subroutine to match the periods of the models ($\rm P^{obs calc}$) with the observed 
+periods $P^{\rm obs}$. Following standard statistical methods, each fit is assigned a fitness parameter calculated the following way:
 
-\begin{equation}
+\begin{eqnarray}
 \label{fiteq1}
-\rm \sigma_{RMS} = \sqrt{\frac{\sum_{1}^{n_{obs}} {(P_{calc}-P_{obs})^2}}{n_{obs}}},
-\end{equation}
+\sigma_{\rm RMS} = \sqrt{\frac{1}{W} \sum_{1}^{n_{\rm obs}} {w_i(P^{\rm calc}_i-P^{\rm obs}_i)^2}}, \\
+W=\frac{n_{\rm obs}-1}{n_{\rm obs}}\sum_{1}^{n_{\rm obs}}w_i
+\end{eqnarray}
 
-\noindent where $\rm n_{obs}$ is the number of periods present in the pulsation spectrum.
+\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ are the inverse square of the uncertainties listed for each period in table \ref{gd}.
+We note that the two shortest period modes have 6000 times the weight of the longest period mode.
+Another way to see this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
+20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get.
+In order to have the same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds.
+In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more.
 
@@
 \citep[e.g.][]{Dehner95,Althaus05} show that at 24{,}000~K, a typical temperature for a DBV, 
-the carbon has not fully settled into the core of the star yet. We expect the helium layer to 
+the carbon has not yet fully settled into the core of the star. We expect the helium layer to 
 be separated into a mixed He/C layer with a pure He layer on top, as shown in Fig. \ref{ffit1}. 
@@
 the edge of the homogeneous carbon and oxygen core (\qfm, as a fraction of stellar mass. 
-For envelope structure, \menv marks the location of the base of the helium layer 
-and \mhe the location where the helium abundance rises to $1$ (see Fig. \ref{ffit1}). 
-\menv and \mhe are mass coordinates, defined as e.g. $M_{\rm env} = -\log(1 - M(r)/M_*)$, 
+For envelope structure, \menv\ marks the location of the base of the helium layer 
+and \mhe\ the location where the helium abundance rises to $1$ (see Fig. \ref{ffit1}). 
+\menv\ and \mhe\ are mass coordinates, defined as e.g. $M_{\rm env} = -\log(1 - M(r)/M_*)$, 
 where $M(r)$ is the mass enclosed in radius r and $M_*$ is the stellar mass.
@@
 \caption{
-{\em Upper panel:} Chemical composition profiles of the best fit model.
-The center of the model is to the left and the surface to the right.
-$q=2$ corresponds to $M_r = 0.99 \: M_*$.
-The vertical axis shows fractional abundances.
+{\em Upper panel:} Chemical composition profiles of the best fit model. The center of the model is 
+to the left and the surface to the right.  $q=2$ corresponds to $M_r = 0.99 \: M_*$. The vertical axis
+shows fractional abundances. 
 {\em Lower panel:} The corresponding \bvf frequency ($\log{N^2}$ on the vertical axis). \label{ffit1}
@@
 
-We started with a master grid (table \ref{fitt1}) chosen so that it covered all relevant 
-area of parameter space and had sufficient resolution to find any region of local minimum in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}.
-We used the minimum resolution that was computationally manageable.
-The master grid involved the computation
+We started with a master grid (Table \ref{fitt1}) chosen so that it covered all relevant 
+area of parameter space and had sufficient resolution to find any region of local minimum 
+in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}. We used the minimum resolution 
+that was computationally manageable. The master grid involved the computation 
 of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
-modes. A fitness map of this initial fit are shown in the left panel of Fig. \ref{ffit2}, and the parameters of the best fit model are listed in table \ref{fitt1}.
+modes. A fitness map of this initial fit are shown in the left panel of Fig. \ref{ffit2}, and the 
+parameters of the best fit model are listed in Table \ref{fitt1}.
 
@@
 
-Before we refine the period-by-period fitting optimization, it is worth stepping back and consider 
-what we can learn from the average period spacing of GD358. The average period spacing provides an asteroseismic measure of the mass and temperature of the star, independent of the details of 
+Before we refine the period-by-period fitting optimization, it is worthwhile to step back and consider 
+what we can learn from the average period spacing of GD358. The average period spacing provides an 
+asteroseismic measure of the mass and temperature of the star, independent of the details of 
 internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
@@
 
-We can use the sequence of 13 consecutive $\ell=1$ modes found in GD358's pulsation spectrum to calibrate our models. 
+We use the sequence of 13 consecutive $\ell=1$ modes found in GD358's pulsation spectrum to calibrate our models. 
 Using the $\ell=1$ sequence of modes, we compute an average period spacing of 39.08 seconds. We call 
 this $\Delta P_{\rm obs}$. For each model in the master grid, we compute an asymptotic period spacing 
-($\Delta P_{\rm calc}$).
-This asymptotic period spacing is calculated by first discarding the 10 lowest $k$ modes.
+($\Delta P_{\rm calc}$). This asymptotic period spacing is calculated by first discarding the 10 lowest $k$ modes. 
 The exact value of 10 is somewhat arbitrary, but it is chosen so that the modes we use in 
@@
 lower $k$ modes. We then fit a line through the set ($k_i$,$P_i$). The slope gives us the asymptotic 
-period spacing in the model. We also calculate the residuals of the fits and discard the models that have residuals above a certain limit. The limit is chosen by checking the procedure 
+period spacing in the model. We also calculate the residuals of the fits and discard the models that have 
+residuals above a certain limit. The limit is chosen by checking the procedure 
 by eye on a few models.
@@
 order for 15 periods to fit reasonably well, the model period list should have a spacing similar to 
-that of the observed period spectrum. It is also somewhat comforting to find that the spectroscopic 
-data point also falls within the swath where the period spacings match (though the best fit model 
-based on the master grid search is further down the valley).
+that of the observed period spectrum.
+The most recent spectroscopic determination of \citet{Koester2013} is far off the valley, at 24,000~K and $0.506^{+0.034)_{-0.051}}$ \msun.
+Previous spectroscopic determinations, such as that of \citet{Bergeron2011}, do fall within the swath where the period spacings match.
+We show the spectroscopic data point of \citet{Bergeron2011} in Fig.
+\ref{ffit2}.
+The best fit model from the period by period fit lies further down the valley.
 
@@
 in the mass-effective temperature plane. The scale is in 10s of seconds, so the worse matches 
-pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 2 \; \rm s$. \label{ffit2}
+pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 2 \; \rm s$.
+We plotted the spectroscopic mass and temperature determinations of \citet{Bergeron2011}, and that of \citet{Koester2013}.
+The latter is off to the left of the plot, and only part of an error bar is visible.
+\label{ffit2}
 }
@@
 
-The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in 
+The parameters for our best fit model based on the refined grid are listed in Table \ref{fitt1} and the periods of that model in 
 Table \ref{gd}. The goodness of fit of the model is \sigrms$=4.22$~s. In Fig. \ref{ffit1}, we show the interior structure of 
@@
 
-We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 
-24000~K \citep{Koester2013} by more than one sigma (the mass matches the spectrosocopy). For reasons discussed in 
-section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the 
-blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting. As we can 
-see from Fig. \ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at 
-lower effective temperature. Structure parameters, especially the location of chemical transitions 
-(with the exception of \menv\ in the case of GD358) are more tightly constrained.
+We analyzed archival data and over a thousand hours of new observations on GD358, together covering a span of 33 years.
+This allowed us to extract 15 frequencies.
+This adds 4 modes to the 11 modes known previously.
+We performed a new asteroseismic fit of GD358 with the new modes and with models that include carbon and oxygen core composition profiles based on the stellar evolution models of \citet{Salaris97}.
 
-In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of 
-parameters able to yield very different fitness number. This is due to the fact that some periods can change values 
-drastically for a small change in a given parameter. The phenomenon is only semi-chaotic, as the period will oscillate 
-between two values. This is good news, because there remains a well defined minimum in parameter space, even if it is a 
-double valued minimum. Any search algorithm that uses a small enough mesh should be able to find the minimum. This 
-phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long 
-consecutive sequence of modes of the same $\ell$ with high resolution grids.
+We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 24000~K \citep{Koester2013} by 2,000~K (4 sigmas).
+Our best fit model has a mass of 0.5438 \msun, a little over one sigma above the spectroscopic mass.
+For reasons discussed in section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting.
+As we can see from Fig.
+\ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at lower effective temperature.
+\emph{However}, the fact that the spectroscopic data point of \citet{Koester2013} falls far off the asymptotic period spacing trend (Fig.
+\ref{ffit2}, right panel) is a concern.
+This is a profound inconsistency that needs to be resolved.
 
-In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so 
-that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, 
-EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of 
-asteroseismic fitting that used a consistent set of models. Unfortunately, GD358 does not fit neatly into the 
-trend (neither does EC20058). It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have 
-thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for 
-GD358 and $-5.94$ for CBS114. Pinning down the proper effective temperature of each star is challenging. To be 
-fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly 
-constrained asteroseimically. At best we can contrast blue edge versus red edge objects.
+In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness number.
+This is due to the fact that some periods can change values drastically for a small change in a given parameter.
+The phenomenon is only semi-chaotic, as the period will oscillate between two values.
+This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
+Any search algorithm that uses a small enough mesh should be able to find the minimum.
+This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
+
+In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
+We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
+Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058).
+It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
+Pinning down the proper effective temperature of each star is challenging.
+To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically.
+At best we can contrast blue edge versus red edge objects.
 
 Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with 
-the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition 
-zones occur \citep{Bischoff-Kim15}. Modern asteroseismic fitting vary parameters attached to the shape of 
-transition zones \citep{Giammichele15}. We refrained from doing this in the present study because we wanted 
-to compare our results with previous studies of DBVs. It is unclear how much of an effect on structure 
+the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur \citep{Bischoff-Kim15}.
+Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.
+We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs.
+It is unclear how much of an effect on structure
 parameters a change in parameterization would have.
+
+With data spanning a long period of time, we learn about the stability of the different modes.
+We find that the shorter period modes tend to be more stable, while the longer period modes tend to vary more in frequency over time.
+\Citet{Bell15} have observed and modeled such stochastic behavior in KIC 4552982, a red edge DAV observed nearly continuously for 1.5 years by \emph{Kepler}.
+In that star, the 361.58 s triplet has sharply defined peaks, while the rest of the modes, with much higher overtone numbers, are less stable.
+The stability of the low k modes is likely due to the fact that they are strongly trapped in the core.
+Unlike their higer k counterparts, they are affected very little by the convection zone near the surface.
 

### 2016-03-16 gd358fit.tex
Made changes to msnew.tex
Almost final edits

@@
 \tablewidth{0pc}
-\tablecaption{List of 15 Periods Used in GD358 Fit.  
+\tablecaption{List of 15 Periods Used in Fitting GD358 and Corresponding Best Fit Periods.  
 \label{gd}
@@
 \tablehead{
-
 \colhead{$k$} & \colhead{Frequency}& \colhead{Period} & \colhead{Uncertainty} & \colhead{Best fit periods}  \\
-\colhead{(\muHz)}  & \colhead{(s)} & \colhead{(\muHz)} & \colhead{(s)} & \colhead{(s)} \\
+\colhead{}  & \colhead{(\muHz)} & \colhead{(s)} & \colhead{(s)} & \colhead{(s)} 
 }
 \startdata
-
-8  &2363.318 & 423.13 & 0.04 & 426.539 \\
-9  &2155.544 & 463.92 & 0.04 & 465.282 \\
-10 &2007.628 & 497.83 & 0.2 & 498.088 \\
-11 &1857.716 & 538.30 & 0.3 & 541.349 \\
-12 &1741.505 & 574.22 & 0.1 & 572.361 \\
-13 &1619.700 & 617.40 & 0.2 & 615.581 \\
-14 &1518.160 & 658.69 & 0.5 & 658.698 \\
-15 &1428.943 & 699.82 & 0.2 & 701.322 \\
-16 &1369.336 & 730.28 & 0.8 & 729.084 \\
-17 &1299.147 & 769.74 & 0.2 & 770.469 \\
-18 &1238.129 & 807.67 & 0.2 & 813.484 \\
-19 &1170.207 & 854.55 & 0.6 & 851.921 \\
-20 &1109.271 & 901.49 & 0.8 & 896.257 \\
-22 &1032.967 & 968.09 & 1.4 & 960.588 \\
-24 &941.333  & 1062.32 & 3.1 & 1056.794\\
+8  &2363.318 & 423.13 & 0.04 & 423.12 \\
+9  &2155.544 & 463.92 & 0.04 & 463.87 \\
+10 &2007.628 & 497.83 & 0.2 & 493.14 \\
+11 &1857.716 & 538.30 & 0.3 & 540.80 \\
+12 &1741.505 & 574.22 & 0.1 & 574.90 \\
+13 &1619.700 & 617.40 & 0.2 & 615.98 \\
+14 &1518.160 & 658.69 & 0.5 & 656.61 \\
+15 &1428.943 & 699.82 & 0.2 & 701.43 \\
+16 &1369.336 & 730.28 & 0.8 & 741.67 \\
+17 &1299.147 & 769.74 & 0.2 & 768.84 \\
+18 &1238.129 & 807.67 & 0.2 & 809.40 \\
+19 &1170.207 & 854.55 & 0.6 & 854.01 \\
+20 &1109.271 & 901.49 & 0.8 & 893.00 \\
+22 &1032.967 & 968.09 & 1.4 & 967.71 \\
+24 &941.333  & 1062.32 & 3.1 & 1051.16\\
 \hline
- &  &  & & $\sigma_{\rm{rms}}$   & 3.12~s\\
+   &         &         & $\sigma_{\rm{rms}}$   & 0.964~s\\
+   &   		 &		   & BIC (${\rm n_{obs}}=15$                 & -0.0303~s \\
 \tableline
 \enddata
-\tablecaption{A list of the 15 periods used in the present fit of GD 358. We also include the corresponding periods 
-from the best fit model (section ref{}). The $k$ identification is listed for each mode. There is strong evidence that 
-all modes belong to an $\ell=1$ sequence. We assume that all the periods listed correspond to the $m=0$ 
-component of any multiplet.\label{t1}}
 \end{deluxetable}

### 2016-03-16 msnew.tex
Almost final edits

@@
 We note that the two shortest period modes have 6000 times the weight of the longest period mode.
-Another way to see this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
+Another way to think about this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get.
@@
 In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more.
+It is, however completely consistent with the relative uncertainty on the periods.
 
@@
 %  {\includegraphics[width=1.0\columnwidth]{ffit1.eps}}
+\epsscale{1.0}
  \plotone{ffit1.eps}
@@
 the mass-effective temperature plane is the fitness parameter defined in equation \ref{fiteq1}. 
-The scale is in seconds. {\it Right panel}: Contour map of the difference between the average 
+{\it Right panel}: Contour map of the difference between the average 
 periods spacing determined from GD 358's periods and the asymptotic period spacing of the models, 
 in the mass-effective temperature plane. The scale is in 10s of seconds, so the worse matches 
-pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 2 \; \rm s$.
-We plotted the spectroscopic mass and temperature determinations of \citet{Bergeron2011}, and that of \citet{Koester2013}.
-The latter is off to the left of the plot, and only part of an error bar is visible.
+pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 5 \; \rm s$.
+We plotted the spectroscopic mass and temperature determinations of \citet{Bergeron2011} (higher mass), and that of \citet{Koester2013} (lower mass).
+The point without error bars corresponds to the best initial fit model.
 \label{ffit2}
@@
 Note that the period spacing is a much weaker constraint than the individual period fit. 
-If one takes 5.0 seconds as an upper limit for goodness of fit, that includes 9 points in the 
+If one takes 5.0 seconds as an upper limit for goodness of fit, that includes 4\% of the points in the 
 period-by-period fit plot (left panel in Fig \ref{ffit2}), but the entire parameter plane 
-for the average period spacing fit plot (right panel). We bypass the difficulty of 
-assigning proper weights to each constraint by taking the average period spacing fit into 
-account as an initial step to refine our fits. We refine our fits by calculating models on 
-a higher resolution grid that fall within the region defined by the two diagonal lines shown 
-in the right panel of Fig. \ref{ffit2} (covering the effective temperature range 25,000~K-27,500~K), then performing a period-by-period fit using 
-equation \ref{fiteq1}.
+for the average period spacing fit plot (right panel).
+In our refined fits, we limit ourselves to a region very near the best fit model found on the initial grid.
+This essentially limits our search to models that already match the average period spacing.
+We avoid sophisticated schemes to calculate the fitness parameter and simply use equation \ref{fiteq1}.
 
@@
 One way to gain a sense of how fine the grid needs to be is to make single 
-parameter cuts through parameter space. Fig.  \ref{ffit3} shows such a cut 
+parameter cuts through parameter space. Fig.  \ref{ffit3} shows such cuts 
 for master grid models. The plot was made by fixing 5 of the 6 parameters 
 to the best fit values of the best initial fit (see table \ref{fitt1}).
-We allowed the effective temperature to vary through the entire range 
-considered for the master grid. The fits seem to settle to a minimum in a 
-smooth way, except for the striking anomaly at 26,600~K. Upon further 
-investigation, we discovered that anomaly to be due to a single period in 
-the pulsation spectrum: the 968~s mode. In the models, that mode appears 
-highly sensitive to some parameters, and in a non-continuous way.
+For some parameters, the fits seem to settle to a minimum in a 
+smooth way, while for others, they exhibit jumps.
+For instance, the spike in the effective temperature plot at 27,800~K is due to a period (around 530~s) that goes away and then comes back.
+The model with the missing period fits poorly compared to the models on either side of it.
+The jump from \sigrms $\sim$ 5 to \sigrms $\sim$ 30 that happens from 28,400~K to 28,600~K is due to a discontinuous change in the period spectrum of the models.
+Namely, the appearance of a new mode between the 710 and 784~s modes of the 28,400~K model.
 
 \begin{figure}
-\epsscale{0.7}
+\epsscale{1.0}
 \plotone{ffit3.eps}
@@
 \caption{
-Dependence of the fitness parameter on effective temperature alone based on 
-the master grid of models. \label{ffit3}
+Dependence of the fitness parameter on different parameters. The 5 parameters other than the one shown 
+on the horizontal axis in each plot are held to fixed values corresponding to the initial best fit model (table \ref{ffit1}).
+The vertical dashed lines mark the ranges considered in the refined fitting.
+For the envelope mass, we went up to \menv = 2.3.
+ \label{ffit3}
 }
@@
 
-This is unsettling, as it is easy to see that one might miss the best fit 
-models if the grid is not fine enough. In order to quantify "fine enough", 
+Discontinuities like these are unsettling, as it is easy to see that one might miss a best fit 
+model if the grid is not fine enough. In order to quantify "fine enough", 
 we ran systematic scans, computing models with 5 parameter fixed and allowing 
@@
 $\Delta M_{\rm env}= \Delta M_{\rm He}=0.01$ dex, $\Delta X_o=0.01$, and $\Delta q_{\rm fm}=0.001$. 
-Results for 4 different parameters are shown in Fig \ref{ffit4}. The figure 
-includes zooms to regions of interest. Other modes also exhibit a behavior 
-similar to the 968~s mode, in different regions of parameter space. For instance, 
-the jumps in \sigrms\ for \qfm\ between 0.3 and 0.4 are due 
-to sudden changes in the 854.5 and 902.5~s modes.
-
 Regardless of the behavior of individual modes in the models as the parameters vary, 
-we can assert from the test above what step sizes will allow us to minimize our risk 
-of missing a minimum. We settled on optimal step sizes of 
-$\Delta {\rm T_{eff}}=20$, $\Delta M_*=0.0002$, $\Delta M_{\rm He}=0.2$, 
-$\Delta X_o=0.2$, and $\Delta q_{\rm fm}=0.01$ for our refined grid. To offset 
-the computational cost, we fixed $M_{\rm env}$ to a canonical value of 
-2.80 \citep{Dehner95}. It is clear from the second panel in Fig. \ref{ffit4} 
-that there is only a weak dependence of the fits on that parameter.
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{ffit4.eps}
-%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
-%  \includegraphics[width=0.9\columnwidth]{ffit4.eps}
-\caption{
-\label{ffit4}
-Dependence of the fitness parameter on different parameters. The 5 parameters other than the one shown 
-on the horizontal axis in each plot are held to fixed values corresponding to the best fit model (table \ref{ffit1}).
-}
-
-\end{figure}
+we can assert what step sizes will allow us to minimize our risk 
+of missing a minimum. We settled on step sizes of 
+$\Delta {\rm T_{eff}}=50$, $\Delta M_*=0.0001$, $\Delta M_{\rm env}=0.1$, $\Delta M_{\rm He}=0.1$, 
+$\Delta X_o=0.1$, and $\Delta q_{\rm fm}=0.005$ for our refined grid.
 
@@
 The parameters for our best fit model based on the refined grid are listed in Table \ref{fitt1} and the periods of that model in 
-Table \ref{gd}. The goodness of fit of the model is \sigrms$=4.22$~s. In Fig. \ref{ffit1}, we show the interior structure of 
-the best fit model, with the corresponding \bvf frequency profile.
+Table \ref{gd}. The goodness of fit of the model is \sigrms$=0.964$~s. We also list
+the Bayes Information Criterion (BIC) number, a statistic that
+normalizes the quality of fits by number of free parameters and
+number of constraints for comparison with other studies. For a discussion applied to this parameter
+study, see \citet{Bischoff-Kim11a}.
+A negative BIC indicates a good quality of fit, given the number of constraints.
+One should keepp in mind that the quality of fit is aided by the fact that some of the periods have large uncertainties.
+
+In Fig.
+\ref{ffit4} we focus on the mass dependence of the fitness parameter to illustrate the effect a finer grid has on the fitting.
+We could have used less of a fine mesh in mass, but with our very fine mesh, we do get a better view of how the discontinuities first shown in Fig.
+\ref{ffit3} behave and that they are not true discontinuities, just large changes in goodness of fit for small changes in mass.
+
+\begin{figure}
+\epsscale{0.7}
+\plotone{ffit4.eps}
+%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
+%  \includegraphics[width=0.9\columnwidth]{ffit3.eps}
+\caption{
+Dependence of the fitness parameter on mass alone based on 
+the master grid of models (dashed line) and the refined mesh (solid line). \label{ffit4}
+}
+\end{figure}
+
+Finally, we show the interior structure of the best fit model in Fig. \ref{ffit1}, with the corresponding \bvf frequency profile.
 

### 2016-03-16 msnew.tex
almost ready to go

@@
 We note that the two shortest period modes have 6000 times the weight of the longest period mode.
-Another way to think about this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
+Another way to think about this is to assume that we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get.
@@
 In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more.
-It is, however completely consistent with the relative uncertainty on the periods.
+It is, however completely consistent with the relative uncertainty on the periods and it provides us with a true measure of the goodness of fit, while accounting for all the data we have.
 
@@
 were very close to the best fit model. We used the period list for a model with parameters 
-${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, 
-fixing $M_{\rm env}$ to -2.80, and including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
+${\rm T_{eff}}=25630$~K, $M_*/M_\odot=0.57065$, \menv $=-2.05$ $M_{\rm He}=-5.55$, $X_o=0.52$, and $q_{\rm fm}=0.192$, including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
 
@@
 described at the end of section \ref{periodspacing}. We are able to recover the best fit parameters adequately, with 
-the top 10 best fit models having parameters 
-${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_\odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 
-10 fits, and $q_{\rm fm}=0.175 \pm 0.5$. The top 10 best fits have \sigrms $\sim$ 0.5~s. We remind the reader that 
-the step sizes in the second phase of the fitting are 20~K for ${\rm T_{eff}}$, 0.2 for $M_{\rm He}$, 0.2 for $X_o$, 
-and 0.01 for $q_{\rm fm}$.
+the all top 5 best fit models having parameters 
+${\rm T_{eff}}=25000$~K, \mhe $=-2.1$, $M_{\rm env}=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a mass ranging between  0.5730 and 0.5734 \msun.
+The best fit model has \sigrms $=0.31$~s.
+We remind the reader that
+the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun for stellar mass, 0.1 for 0.1 for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
 
@@
 
-We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 24000~K \citep{Koester2013} by 2,000~K (4 sigmas).
-Our best fit model has a mass of 0.5438 \msun, a little over one sigma above the spectroscopic mass.
-For reasons discussed in section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting.
-As we can see from Fig.
-\ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at lower effective temperature.
-\emph{However}, the fact that the spectroscopic data point of \citet{Koester2013} falls far off the asymptotic period spacing trend (Fig.
+WE find a best fit effective temperature of 23,650~K and a mass of 0.5706 \msun for GD358.
+While the temperature is close to the recent spectroscopic determination of 24000~K \citep{Koester2013}, the mass is over one sigma above the spectroscopic mass.
+On the other hand, the mass matches almost exactly that found by \citet{Bergeron2011} (but the effective temperature is low).
+The fact that the spectroscopic data point of \citet{Koester2013} is far off the asymptotic period spacing trend (Fig.
 \ref{ffit2}, right panel) is a concern.
-This is a profound inconsistency that needs to be resolved.
 
@@
 We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
-Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058).
-It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114.
+Among the 4, cooler best fit models do exhibit thicker pure helium envelopes.
 Pinning down the proper effective temperature of each star is challenging.
-To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically.
-At best we can contrast blue edge versus red edge objects.
+To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained.
+We show the relationship between asteroseismic effective temperature and pure helium layer mass in Fig.
+\ref{ffit5}.
+Stellar mass also comes into play and ideally, we would like all 4 models to have the same mass.
+The models range in mass from 0.525 (Ec20058) to 0.640 \msun (CBS114).
+More detailed stellar evolution calculations would have to be performed in order to assess the significance of the trend observed with these 4 DBVs.
+
+\begin{figure}
+\epsscale{0.7}
+\plotone{ffit5.eps}
+%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
+%  \includegraphics[width=0.9\columnwidth]{ffit3.eps}
+\caption{
+Relationship between effective temperature and pure helium layer mass in 4 DBVs fitted using similar models as GD358 in the present study. \label{ffit5}
+}
+\end{figure}
 
@@
 We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs.
-It is unclear how much of an effect on structure
-parameters a change in parameterization would have.
+It is unclear how much of an effect on structure parameters a change in parameterization would have.
 
@@
 Unlike their higer k counterparts, they are affected very little by the convection zone near the surface.
-
-%We have performed and published a preliminary fit of the star (Hawaii proceedings), where we found a temperature of 23,600 K, a mass of 0.605 $M_\odot$, \menv = -2.40, \mhe = -5.20, a central oxygen abundance of 0.99, and \qfm = 0.50.
-In the preliminary fits, the period list was not finalized and we did not include the 1065.260 s mode, because it was difficult to fit and we did not have a positive ell identification for the mode.
-It might be disheartening to observe such a big difference in the best fit parameters by just including or excluding one mode out of 15, but it is worth noting that the thickness of the pure helium layer was not affected much by the inclusion or exclusion of the 15th mode and refinements done in the search in this work.
-We emphasize again that in the final stages of our fitting for this work, we fixed the envelope mass to -2.80.
-%
-%In section \ref{periodspacing}, we discussed the degeneracy in the determination of the mass and effective temperature parameters.
-That degeneracy means that a unique determination of effective temperature and mass is not always possible.
-The fits are also marginally sensitive to the central oxygen abundance.
-What is surprising is the big difference in the determination of the location of the edge of the homogeneous C/O core from our preliminary fits to the refined fits presented in this paper.
-If we take the best fit model from the preliminary work and include the 15th period when calculating the fitness number, the quality of the fit becomes significantly worse (2.84 s to 5.12 s).
-We would not expect a k=24 mode to be strongly trapped in the core, quite the contrary.
-This could be due to a core-envelope symmetry \citep{Montgomery03}, but more detailed studies would be required to make a more definitive statement.
-We should also keep in miind that the period lists used in the fits were close but not identical.
 

### 2016-03-17 msnew.tex
Draft ready for review

@@
 The surface gravity translates to a mass range of 0.455 to 0.540 \msun.
-Our best fit model is slightly more massive and much hotter (by 2,000~K) than the most recent spectroscopy indicates.
-We find a pure helium layer mass of $10^{-5.40}$, consistent with a red edge object when compared with other DBVs analyzed using the same models.
+Our best fit model has a temperature of 23,650~K and a mass of 0.5706 \msun ~.
+That is slightly more massive than what the most recent spectroscopy suggests.
+We find a pure helium layer mass of $10^{-5.50}$, consistent with the outward diffusion of helium over time.
 
@@
 The basic method in our asteroseismic fitting consists of calculating grids of white dwarf models and 
-running a fitting subroutine to match the periods of the models ($\rm P^{obs calc}$) with the observed 
+running a fitting subroutine to match the periods of the models ($\rm P^{calc}$) with the observed 
 periods $P^{\rm obs}$. Following standard statistical methods, each fit is assigned a fitness parameter calculated the following way:
@@
 area of parameter space and had sufficient resolution to find any region of local minimum 
-in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}. We used the minimum resolution 
+in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}. We used the maximum resolution 
 that was computationally manageable. The master grid involved the computation 
@@
 that of the observed period spectrum.
-The most recent spectroscopic determination of \citet{Koester2013} is far off the valley, at 24,000~K and $0.506^{+0.034)_{-0.051}}$ \msun.
+The most recent spectroscopic determination of \citet{Koester2013} is far off the valley, at 24,000~K and $0.506^{+0.034}_{-0.051}$ \msun.
 Previous spectroscopic determinations, such as that of \citet{Bergeron2011}, do fall within the swath where the period spacings match.
-We show the spectroscopic data point of \citet{Bergeron2011} in Fig.
-\ref{ffit2}.
-The best fit model from the period by period fit lies further down the valley.
 
@@
 \begin{figure}
-\epsscale{0.7}
+\epsscale{1.0}
 \plotone{ffit2.eps}
@@
 periods spacing determined from GD 358's periods and the asymptotic period spacing of the models, 
-in the mass-effective temperature plane. The scale is in 10s of seconds, so the worse matches 
+in the mass-effective temperature plane. The scale is in 10ths of seconds, so the worse matches 
 pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 5 \; \rm s$.
@@
 Note that the period spacing is a much weaker constraint than the individual period fit. 
-If one takes 5.0 seconds as an upper limit for goodness of fit, that includes 4\% of the points in the 
+If one takes 5.0 seconds as an upper limit for goodness of fit, that includes 4\% of the models in the 
 period-by-period fit plot (left panel in Fig \ref{ffit2}), but the entire parameter plane 
@@
 The model with the missing period fits poorly compared to the models on either side of it.
-The jump from \sigrms $\sim$ 5 to \sigrms $\sim$ 30 that happens from 28,400~K to 28,600~K is due to a discontinuous change in the period spectrum of the models.
+The jump from \sigrms $\sim$ 5 s to \sigrms $\sim$ 30 s that happens from 28,400~K to 28,600~K is due to a discontinuous change in the period spectrum of the models.
 Namely, the appearance of a new mode between the 710 and 784~s modes of the 28,400~K model.
@@
 The vertical dashed lines mark the ranges considered in the refined fitting.
-For the envelope mass, we went up to \menv = 2.3.
+For the envelope mass, we went from \menv = -2.0 to -2.3.
  \label{ffit3}
@@
 we can assert what step sizes will allow us to minimize our risk 
-of missing a minimum. We settled on step sizes of 
-$\Delta {\rm T_{eff}}=50$, $\Delta M_*=0.0001$, $\Delta M_{\rm env}=0.1$, $\Delta M_{\rm He}=0.1$, 
+of missing a minimum, while minimizing the number of models to compute. We settled on step sizes of 
+$\Delta {\rm T_{eff}}=50$~K, $\Delta M_*=0.0001 M_\odot$, $\Delta M_{\rm env}=\Delta M_{\rm He}=0.1$ dex,  
 $\Delta X_o=0.1$, and $\Delta q_{\rm fm}=0.005$ for our refined grid.
@@
 A negative BIC indicates a good quality of fit, given the number of constraints.
-One should keepp in mind that the quality of fit is aided by the fact that some of the periods have large uncertainties.
+One should keepp in mind that the quality of fit is aided by the fact that some of the observed periods have large uncertainties.
 
@@
 We remind the reader that
-the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun for stellar mass, 0.1 for 0.1 for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
+the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun ~ for stellar mass, 0.1 dex for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
 
@@
 We analyzed archival data and over a thousand hours of new observations on GD358, together covering a span of 33 years.
-This allowed us to extract 15 frequencies.
-This adds 4 modes to the 11 modes known previously.
-We performed a new asteroseismic fit of GD358 with the new modes and with models that include carbon and oxygen core composition profiles based on the stellar evolution models of \citet{Salaris97}.
+With data spanning such a long period of time, we learn about the stability of the different modes.
+We find that the shorter period modes tend to be more stable, while the longer period modes tend to vary more in frequency over time.
+\citet{Bell15} have observed and modeled such stochastic behavior in KIC 4552982, a red edge DAV observed nearly continuously for 1.5 years by \emph{Kepler}.
+In that star, the 361.58 s triplet has sharply defined peaks, while the rest of the modes, with much higher overtone numbers, are less stable.
+The stability of the low k modes is likely due to the fact that they are strongly trapped in the core.
+Unlike their higer k counterparts, they are affected very little by the convection zone near the surface.
 
-WE find a best fit effective temperature of 23,650~K and a mass of 0.5706 \msun for GD358.
+In analyzing the data, we found 4 new modes, adding to the 11 modes known previously.
+With these 15 modes, we performed a new asteroseismic fit of GD358 with models that include carbon and oxygen core composition profiles based on the stellar evolution models of \citet{Salaris97}.
+We find a best fit effective temperature of 23,650~K and a mass of 0.5706 \msun ~ for GD358.
 While the temperature is close to the recent spectroscopic determination of 24000~K \citep{Koester2013}, the mass is over one sigma above the spectroscopic mass.
 On the other hand, the mass matches almost exactly that found by \citet{Bergeron2011} (but the effective temperature is low).
-The fact that the spectroscopic data point of \citet{Koester2013} is far off the asymptotic period spacing trend (Fig.
-\ref{ffit2}, right panel) is a concern.
-
-In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness number.
-This is due to the fact that some periods can change values drastically for a small change in a given parameter.
-The phenomenon is only semi-chaotic, as the period will oscillate between two values.
-This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
-Any search algorithm that uses a small enough mesh should be able to find the minimum.
-This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
+The spectroscopic data point of \citet{Koester2013} is somewhat off the asymptotic period spacing trend (Fig.
+\ref{ffit2}, right panel).
 
@@
 We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
-Among the 4, cooler best fit models do exhibit thicker pure helium envelopes.
-Pinning down the proper effective temperature of each star is challenging.
-To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained.
-We show the relationship between asteroseismic effective temperature and pure helium layer mass in Fig.
-\ref{ffit5}.
-Stellar mass also comes into play and ideally, we would like all 4 models to have the same mass.
-The models range in mass from 0.525 (Ec20058) to 0.640 \msun (CBS114).
+We find that cooler best fit models have thicker pure helium envelopes (Fig.
+\ref{ffit5}), in accordance with the outward diffusion of helium over time.
+To be consistent, we used the effective temperature found through the asteroseismic fitting of each star.
+Stellar mass also comes into play in diffusion.
+Ideally, we would like all 4 models to have the same mass.
+The models range in mass from 0.525 (EC20058) to 0.640 \msun ~ (CBS114).
 More detailed stellar evolution calculations would have to be performed in order to assess the significance of the trend observed with these 4 DBVs.
@@
 Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with 
-the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur \citep{Bischoff-Kim15}.
+the theory of non-radial oscillations, the shapes of the transition zones matter as much as where they occur \citep{Bischoff-Kim15}.
 Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.
@@
 
-With data spanning a long period of time, we learn about the stability of the different modes.
-We find that the shorter period modes tend to be more stable, while the longer period modes tend to vary more in frequency over time.
-\Citet{Bell15} have observed and modeled such stochastic behavior in KIC 4552982, a red edge DAV observed nearly continuously for 1.5 years by \emph{Kepler}.
-In that star, the 361.58 s triplet has sharply defined peaks, while the rest of the modes, with much higher overtone numbers, are less stable.
-The stability of the low k modes is likely due to the fact that they are strongly trapped in the core.
-Unlike their higer k counterparts, they are affected very little by the convection zone near the surface.
+In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness parameters.
+This is due to the fact that some periods can change values drastically for a small change in a given parameter.
+The phenomenon is only semi-chaotic, as the period will oscillate between two values.
+This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
+Any search algorithm that uses a small enough mesh should be able to find the minimum.
+This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
 

### 2016-08-06 msnew.tex
Revised, including Mike's comments
Sections 1, 5-7

@@
 dwarfs, with most of the remaining 80\% consisting of their hydrogen atmosphere (DA) 
-cousins. The bifurcation into two spectral classes is thought to occur during post-AGB 
-evolution when, in some cases, a very late thermal pulse burns off the residual hydrogen 
+cousins. One theory behind the bifurcation into two spectral classes is that during post-AGB evolution, a very late thermal pulse can burn off the residual hydrogen 
 in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
@@
 \citep{Koester2013}. GD358's pulsation spectrum contains a series of independent 
-modes, many with complex frequency structure.  Models involving magnetic fields and oblique rotation 
-have been proposed to explain that structure \citep{Montgomery10}.
+radial overtones, many with complex frequency structure.
+For one epoch of data taken during a WET run, models involving magnetic fields and oblique rotation have been proposed to explain such structure \citep{Montgomery10}.
 
@@
 frequencies in this complex star. These new observations have identified additional 
-periods in GD358's pulsation spectrum, bringing the total known modes to 15. Thirteen of 
+periods in GD358's pulsation spectrum, bringing the total known independent radial overtones to 15. Thirteen of 
 these modes belong to a consecutive $\ell=1$ sequence, the longest sequence observed 
@@
 
-Paradoxally, among the DBVs with enough detected periods to be fitted 
+Paradoxically, among the DBVs with enough detected periods to be fitted 
 asteroseismically, GD358 is the only one that has not been analyzed using the complex 
@@
 
-To compute our models, we used the White Dwarf Evolution Code (WDEC). The WDEC evolves hot 
-polytrope models from temperatures above 100{,}000~K down to the temperature of our choice. 
-Models in the temperature range of interest for the present study are thermally relaxed 
-solutions to the stellar structure equations. Each model we compute for our grids is the result 
+To compute our models, we used the White Dwarf Evolution Code (WDEC).
+The WDEC uses hot  and self-consistently allows them to relax to be solutions of the equations of stellar structure with the temperature of our choice.
+polytrope models with temperatures above 100{,}000~K as starting model and numericaly evolves them until they are thermally relaxed 
+solutions to the stellar structure equations and have the temperature of our choice.
+The mass is also fixed as an input, and so is the internal chemical composition profiles (no mass loss, no time dependent diffusion of elements).
+Each model we compute for our grids is the result
 of such an evolutionary sequence. The WDEC is described in detail in \citet{Lamb75} and 
@@
 
-In our asteroseismic fits, we initially varied six parameters; the effective temperature, 
+In our asteroseismic fits, we initially varied six parameters: the effective temperature, 
 the mass and four structure parameters. There are two parameters associated with the shapes 
@@
 \label{fiteq2}
-\Delta P = \frac{\pi}{\ell(\ell + 1)^{1/2}}\left[\int_{r_1}^{r_2}\frac{N}{r}dr\right]^{-1},
+\Delta P = \frac{\pi}{\sqrt{\ell(\ell + 1)}}\left[\int_{r_1}^{r_2}\frac{N}{r}dr\right]^{-1},
 \end{equation}
@@
 Dependence of the fitness parameter on different parameters. The 5 parameters other than the one shown 
-on the horizontal axis in each plot are held to fixed values corresponding to the initial best fit model (table \ref{ffit1}).
+on each plot are held to fixed values corresponding to the initial best fit model (table \ref{ffit1}).
 The vertical dashed lines mark the ranges considered in the refined fitting.
@@
 
-\subsection{Validation of the Fitting Method}
+\subsection{Validation of the Fitting Method and Error Estimation}
 
@@
 the all top 5 best fit models having parameters 
-${\rm T_{eff}}=25000$~K, \mhe $=-2.1$, $M_{\rm env}=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a mass ranging between  0.5730 and 0.5734 \msun.
+${\rm T_{eff}}=25000$~K, \menv $=-2.1$, \mhe $=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a mass ranging between  0.5730 and 0.5734 \msun.
 The best fit model has \sigrms $=0.31$~s.
@@
 the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun ~ for stellar mass, 0.1 dex for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
+
+This test also allows us to place minimum error bars on at least some of the parameters found: $\pm 600$ ~ K in effective temperature, 0.05 and 0.02 dex on \menv and \mhe respectively, 0.02 on $X_o$, and 0.002 on $q_{\rm fm}$.
 
@@
 
-In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
+In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14,Giammichele17}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
 We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
@@
 To be consistent, we used the effective temperature found through the asteroseismic fitting of each star.
-Stellar mass also comes into play in diffusion.
+
+%There is one caveat to drawing conclusions from Fig.
+\ref{ffit5}.
+The initial amount of helium in the envelope depends on the mass of the progenitor star and its evolution, with more massive progenitors producing more massive white dwarfs according to the initial-final mass relation.
+Therefore, in order to isolate the effect of diffusion on the mass of the pure helium layer, one would have to consider a single white dwarf mass.
+However, the white dwarf mass distribution is known to be tight, with a range of progenitor masses yielding a narrow range of white dwarf masses.
+We do not believe that our precision in the asteroseismic analyses are at the level where we can use the relationship depicted in Fig.
+\ref{ffit5} to draw quantitative conclusions where the effect of white dwarf mass would matter.
+%
+%Stellar mass also comes into play in diffusion.
 Ideally, we would like all 4 models to have the same mass.
@@
 
-In fitting GD358, we discovered that the best fit parameter space was semi-chaotic, with two very close sets of parameters able to yield very different fitness parameters.
+In fitting GD358, we discovered that two very close sets of parameters were able to yield very different fitness parameters.
 This is due to the fact that some periods can change values drastically for a small change in a given parameter.
-The phenomenon is only semi-chaotic, as the period will oscillate between two values.
-This is good news, because there remains a well defined minimum in parameter space, even if it is a double valued minimum.
+The periods tend to oscillate between two values and there remains a well defined minimum in parameter space, even if it is a double valued minimum.
 Any search algorithm that uses a small enough mesh should be able to find the minimum.

### 2016-08-15 msnew.tex
Added a paragraph about convection zone influence on modes (Mike's poster) updated noise figure, changed 2015 to 2016, fixed a few typos

@@
 M.~H.~Montgomery\altaffilmark{3,4},
+H.~L. Shipman\altaffilmark{2,3},
 Samuel~T.~Harrold\altaffilmark{4},
@@
 D.~Peters\altaffilmark{5},
-A.~V.~Kusakin\altaffilmark{6},
-A.~V.~Sergeev\altaffilmark{7},
-M.~Andreev\altaffilmark{7},
-A.~Maksim\altaffilmark{7},
-S. Velichko\altaffilmark{7}
-R.~Janulis\altaffilmark{8},
-F.~Ali\c cavu\c s\altaffilmark{9},
-N. Horoz\altaffilmark{9},
-S.~Zola\altaffilmark{10,11},
-W.~Og{\l}oza\altaffilmark{10,11},
-D.~Koziel-Wierzbowska{10,11},
-T.~Kundera\altaffilmark{10,11},
-D. Jableka\altaffilmark{10,11},
-B. Debski\altaffilmark{10,11},
-S. Meingast\altaffilmark{12}
+P.~A. Bradley\altaffilmark{6},
+S.-L. Kim\altaffilmark{7},
+X.~J.~Jiang\altaffilmark{8},
+Y-N.~Mao\altaffilmark{8},
+A.~V.~Kusakin\altaffilmark{9},
+A.~V.~Sergeev\altaffilmark{10,11},
+M.~Andreev\altaffilmark{10,11},
+A.~Maksim\altaffilmark{10,11},
+S. Velichko\altaffilmark{12},
+R.~Janulis\altaffilmark{12},
+E.~Pakstiene\altaffilmark{12},
+F.~Ali\c cavu\c s\altaffilmark{13},
+N. Horoz\altaffilmark{13},
+S.~Zola\altaffilmark{14,15},
+W.~Og{\l}oza\altaffilmark{14,15},
+D.~Koziel-Wierzbowska\altaffilmark{14,15},
+T.~Kundera\altaffilmark{14,15},
+D. Jableka\altaffilmark{14,15},
+B. Debski\altaffilmark{14,15},
+S. Meingast\altaffilmark{16},
+T. Nagel\altaffilmark{17},
+L. Loebling\altaffilmark{17},
+C. Heinitz\altaffilmark{17},
+D. Hoyer\altaffilmark{17},
+Zs. Bogn\'ar\altaffilmark{18}
 }
@@
 Paintbrush, Waco, TX 76705; chandler@vvm.com}
-\altaffiltext{6}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
-\altaffiltext{7}{Ukrainian National Academy of Sciences, Main Astronomical
-Observatory, Golosiiv, Kiev 022 252650; sergeev@terskol.com }
-\altaffiltext{8}{Institute of Theoretical Physics and Astronomy, Vilnius
+\altaffiltext{7}{Korea Astronomy and Space Science Institute, Daejeon 34055, Korea}
+\altaffiltext{8}{National Astronomical Observatories, Academy of Sciences, Beijing 10012, People's Republic of
+China; xjjiang@bao.ac.cn}
+\altaffiltext{9}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
+\altaffiltext{10}{Ukrainian National Academy of Sciences, International Center for Astronomical,
+Medical and Ecological Research, 27, Akademika Zabolotnoho Ave., 03680 Kyiv, Ukraine; sergeev@terskol.com }
+\altaffiltext{11}{Russian Academy of Sciences, Institute of Astronomy, Terskol Branch, 81, Elbrus Ave., ap. 33, Tyrnyauz,
+Kabardino-Balkaria Republic, 361623, Russian Federation; sergeev@terskol.com}
+\altaffiltext{12}{Institute of Theoretical Physics and Astronomy, Vilnius
 University, Vilnius, Lithuania; jr@itpa.lt}
-\altaffiltext{9}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
-\altaffiltext{10}{Astronomical Observatory of the Jagiellonian University, ul. Orla
+\altaffiltext{13}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
+\altaffiltext{14}{Astronomical Observatory of the Jagiellonian University, ul. Orla
 171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
-\altaffiltext{11}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
+\altaffiltext{15}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
 Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
-\altaffiltext{12}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}
+\altaffiltext{16}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}
+\altaffiltext{17}{Institut fuer Astronomie und Astrophysik, Kepler Center for Astro and Particle Physics,
+Eberhard Karls Universitaet Tuebingen, Sand 1, 72076 Tuebingen Germany; nagel@astro.uni-tuebingen.de}
+\altaffiltext{18}{Konkoly Observatory, MTA CSFK, Konkoly Thege M. u. 15-17, H-1121 Budapest, Hungary}
 
@@
 \begin{abstract}
-We report on the analysis of 33 years of photometric observations of the pulsating
+We report on the analysis of 34 years of photometric observations of the pulsating
 helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
-and 1105.1 hours of new observations from 2007-2015. From this data set, we extract 15 frequencies 
+and 1195.2 hours of new observations from 2007-2016. From this data set, we extract 15 frequencies 
 representing g-mode pulsation modes, adding 4 modes to the 11 modes 
@@
 instability strip, with a spectroscopic temperature of \teff\ $=24000\pm500$ ~K and \logg\ $=7.8$ 
-\citep{Koester2013}. GD358's pulsation spectrum contains a series of independent 
+\citep{Nitta12, Koester2013}. GD358's pulsation spectrum contains a series of independent 
 radial overtones, many with complex frequency structure.
@@
 In Section \ref{freq}, we establish the framework for frequency identification, and present the 
-list of frequencies used for the asteroseismic investigation.
-We perform further analysis of the observed frequencies in Section \ref{analysis}, and motivate the $\ell$ and $m$ identification of the modes.
-We present the asteroseismic fitting of GD358's pulsation spectrum in section \ref{fitting}, present the results in section \ref{results} and discuss our results in section \ref{discussion}.
+list of frequencies used for the asteroseismic investigation. We perform further analysis of the observed 
+frequencies in Section \ref{analysis}, and motivate the $\ell$ and $m$ identification of the modes. 
+We present the asteroseismic fitting of GD358's pulsation spectrum in section \ref{fitting}, present 
+the results in section \ref{results} and discuss our results in section \ref{discussion}.
 
@@
 Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
-New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
-2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
-multisite WET campaigns \citep{wet90}.
+New observations presented here include 278 individual observing runs (1105.1 hrs) spanning 
+2007-2016 (Table \ref{journal}). Each season of observations was obtained as part of 
+multi-site WET campaigns \citep{wet90}.
 
@@
 \plotone{terskol}
-\caption{Light curve of GD358 obtained with the Peak Terskol 2.0 m telescope.  Each point corresponds 
+\caption{Light curve of GD358 obtained with the Peak Terksol 2.0 m telescope.  Each point corresponds 
 to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
@@
 The complexities associated with GD358's pulsations (see Section \ref{freq}) led us to also 
-re-reduce all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
+re-reduce all available archival data \citep{Provencal09, Bradley04, Kepler03, Winget94, Winget82} to
 insure continuity in methodology. The final result is a series of light curves 
-for each observing season between 1982 and 2015. 
+for each observing season between 1982 and 2016. 
 For the new observations, 2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 
-2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. 
+2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, 2015 55 hrs and 2016 90.6 hrs. 
 Our coverage is not complete, and this incompleteness produces spectral leakage in the 
@@
 are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
-as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
+as a function of frequency for the 2007-2016 observing seasons. A similar plot for the 
 archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
@@
 \plotone{noise}
-\caption{A comparison of the average noise as a function of frequency for the 2007-2015 observing 
+\caption{A comparison of the average noise as a function of frequency for the 2007-2016 observing 
 seasons.  Each data set was prewhitened by its dominant frequencies.  The noise levels for each 
@@
 discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
-modulation is given in \citep{Provencal09}. Our final identifications of independent frequencies
+modulation is given in \citet{Provencal09}. Our final identifications of independent frequencies
 detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.
@@
 
-\subsection{Frequencies Distribution}
-
+\subsection{Frequency Distribution}
 Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
@@
 \begin{figure}
-\epsscale{0.8}
+\epsscale{0.9}
 %\plottwo{gd358multif_2015.eps}{gd358multi.eps}
@@
 Fig.~\ref{schematic} presents a schematic representation of GD358's 
-independent frequencies detected between 1982 and 2015.  
+independent frequencies detected between 1982 and 2016.  
 The features of asteroseismic importance are the localized bands between 900 and 2400
-\muHz\ (1100 and 400 s). We interpret the bands to represent a series of radial overtone $k$. The bands
+\muHz\ (1100 and 400 s). We interpret the bands to represent a series of modes of radial overtone $k$. The bands
 themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
@@
 exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
-from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
-distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
-most likely the result of some process producing amplitude and/or frequency modulation that obscures 
-any underlying signatures of rotational splitting.
-
+from \citet{Provencal09}), we find no clear evidence of stable multiplet structure in the frequency 
+distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). This does not imply that the 
+structures found by \cite{Winget94}, \cite{Kepler03}, \cite{Montgomery10} and others are not real. In 
+particular, it is clear that the $k=12$ mode can be explained by the oblique rotation model during 2006. However, 
+previous work represents short snapshots of GD358. When examined over timescales of decades, these structures 
+do not regularly recur, and so cannot be interpreted as simple rotational splitting. The lower frequency band widths 
+are most likely the result of various processes producing amplitude and/or frequency modulation that obscures any 
+underlying signatures of rotational splitting. 
 \begin{figure}
@@
 Although the observational timebases and coverage are quite different (20 continuous months 
-for KIC4552982 vs 33 incomplete years for GD358), our data presents the opportunity to investigate this 
+for KIC4552982 vs 34 incomplete years for GD358), our data presents the opportunity to investigate this 
 for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
@@
 
-A second interesting behavior is given by the distribution of average amplitudes for the bands 
-(Fig~\ref{schematic}. In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
+\citet{Mont2016} recently outlined a possible explanation for the behavior seen in the low frequency modes
+of these cool DAVs that should also apply to GD358. White dwarfs pulsate in nonradial g-modes. As a DBV such as 
+GD358 pulsates, it experiences local surface temperature variations as large as 3000 K.  The temperature 
+variation affects different modes in different ways.  An appropriate analogy is to consider each mode's 
+propagation region as a box with a lid. The box is defined as the region where the mode frequency is 
+less than both the buoyancy (Brunt-V{\"a}is{\"a}l{\"a}) and acoustic (Lamb) frequencies.  The box's lid 
+represents the mode's outer turning point. For short period modes (such as $k=8$ and $k=9$ in GD358), the 
+lid is defined by the acoustic frequency, which is relatively insensitive to surface temperature variations. 
+As the star pulsates, the box will not change, so these modes should be stable.  For the longer period modes, 
+the lid of the box is defined by the buoyancy frequency, which goes to zero at the base of the surface 
+convection zone. This is the important point: for longer period modes, the box lid
+is actually defined by the base of the convection zone, which is very sensitive to local temperature variations.  
+As GD358 pulsates, its convection zone deepens and thins in response to the local temperature variations. 
+In our analogy, the lid of the box moves, effectively changing the characteristics of the box. Long period modes with 
+outer turning points defined by the base of the convection zone should be perturbed and this is indeed 
+what we see in GD358.
+
+An additional interesting behavior is given by the distribution of average amplitudes for the bands 
+(Fig~\ref{schematic}). In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
 at amplitudes above 4 mma. The band at 1369 \muHz\ is also only observed at lower amplitudes. Interestingly, 
@@
 
-In broad brush strokes, the observed global pulsations involve the whole star, but each pulsation samples the star
-in slightly different ways.  For example, modes with lower frequencies (higher radial $k$ values) preferentially 
-sample the outer layers, while modes with higher frequencies (lower radial $k$ values) have outer turning points 
-that are farther from the surface, and so sample the deeper interior. It makes intuitive sense that lower 
-frequency modes would be affected by processes confined to the outer stellar atmosphere. We speculate that the 
+To summarize this section in broad brush strokes, the observed global pulsations involve the whole star, 
+but each pulsation samples the star in slightly different ways.  Modes with lower frequencies 
+(higher radial $k$ values) preferentially sample the outer layers, while modes with higher frequencies 
+(lower radial $k$ values) have outer turning points that are farther from the surface, and so sample the 
+deeper interior. It makes intuitive sense that lower frequency modes would be affected by processes 
+confined to the outer stellar atmosphere, such as the convection zone. We speculate that the 
 observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface
@@
 \citep{Kotak02, Castanheira05}. It is important to further investigate these identifications 
-as we initiate an indepth asteroseismic investigation.
+as we initiate an in depth asteroseismic investigation.
 
@@
 
-Finally, given the $l$=1 identification and the lack of definite multiplet structure for the higher 
+Finally, given the $l$=1 identification and the lack of definitive multiplet structure for the lower 
 frequency modes, the best way to determine the central frequency for each band is simply to 
@@
 running a fitting subroutine to match the periods of the models ($\rm P^{calc}$) with the observed 
-periods $P^{\rm obs}$. Following standard statistical methods, each fit is assigned a fitness parameter calculated the following way:
+periods $P^{\rm obs}$. Following standard statistical methods, each fit is assigned a fitness 
+parameter calculated the following way:
 
@@
 
-\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ are the inverse square of the uncertainties listed for each period in table \ref{gd}.
-We note that the two shortest period modes have 6000 times the weight of the longest period mode.
-Another way to think about this is to assume that we have a calculated period that matches the highest period mode very poorly, being 20 seconds away.
-20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get.
-In order to have the same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds.
+\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ 
+are the inverse square of the uncertainties listed for each period in table \ref{gd}. We note that the two 
+shortest period modes have 6000 times the weight of the longest period mode. Another way to think about this 
+is to assume that we have a calculated period that matches the highest period mode very poorly, 
+being 20 seconds away. 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the 
+relevant area of parameter space and so it is the worse period fit one can get. In order to have the 
+same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds. 
 In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more. 
-It is, however completely consistent with the relative uncertainty on the periods and it provides us with a true measure of the goodness of fit, while accounting for all the data we have.
+It is, however completely consistent with the relative uncertainty on the periods and it provides us with 
+a true measure of the goodness of fit, while accounting for all the data we have.
 
@@
 The WDEC uses hot  and self-consistently allows them to relax to be solutions of the equations of stellar structure with the temperature of our choice.
-polytrope models with temperatures above 100{,}000~K as starting model and numericaly evolves them until they are thermally relaxed 
+polytrope models with temperatures above 100{,}000~K as starting model and numerically evolves them until they are thermally relaxed 
 solutions to the stellar structure equations and have the temperature of our choice.
@@
 according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
-given by (Unno et al. 1989)
+given by \citet{Unno89}.
 
@@
 
-We use the sequence of 13 consecutive $\ell=1$ modes found in GD358's pulsation spectrum to calibrate our models. 
+We use the sequence of 13 consecutive $\ell=1$ modes found in GD358's pulsation spectrum to calibrate our models (Table~\ref{gd}). 
 Using the $\ell=1$ sequence of modes, we compute an average period spacing of 39.08 seconds. We call 
@@
 order for 15 periods to fit reasonably well, the model period list should have a spacing similar to 
-that of the observed period spectrum.
-The most recent spectroscopic determination of \citet{Koester2013} is far off the valley, at 24,000~K and $0.506^{+0.034}_{-0.051}$ \msun.
-Previous spectroscopic determinations, such as that of \citet{Bergeron2011}, do fall within the swath where the period spacings match.
+that of the observed period spectrum. The most recent spectroscopic determination of \citet{Koester2013} 
+is far off the valley, at 24,000~K and $0.506^{+0.034}_{-0.051}$ \msun. Previous spectroscopic determinations, 
+such as that of \citet{Bergeron2011}, do fall within the swath where the period spacings match.
 
@@
 pictured on the plot have $\left|\Delta P_{\rm obs}- \Delta P_{\rm calc}\right| \sim 5 \; \rm s$. 
-We plotted the spectroscopic mass and temperature determinations of \citet{Bergeron2011} (higher mass), and that of \citet{Koester2013} (lower mass).
-The point without error bars corresponds to the best initial fit model.
-\label{ffit2}
+We plotted the spectroscopic mass and temperature determinations of \citet{Bergeron2011} (higher mass), 
+and that of \citet{Koester2013} (lower mass). The point without error bars corresponds to the 
+best initial fit model. \label{ffit2}
 }
@@
 period-by-period fit plot (left panel in Fig \ref{ffit2}), but the entire parameter plane 
-for the average period spacing fit plot (right panel).
-In our refined fits, we limit ourselves to a region very near the best fit model found on the initial grid.
-This essentially limits our search to models that already match the average period spacing.
-We avoid sophisticated schemes to calculate the fitness parameter and simply use equation \ref{fiteq1}.
+for the average period spacing fit plot (right panel). In our refined fits, we limit ourselves to a 
+region very near the best fit model found on the initial grid. This essentially limits our search 
+to models that already match the average period spacing. We avoid sophisticated schemes to calculate 
+the fitness parameter and simply use equation \ref{fiteq1}.
 
@@
 For some parameters, the fits seem to settle to a minimum in a 
-smooth way, while for others, they exhibit jumps.
-For instance, the spike in the effective temperature plot at 27,800~K is due to a period (around 530~s) that goes away and then comes back.
-The model with the missing period fits poorly compared to the models on either side of it.
-The jump from \sigrms $\sim$ 5 s to \sigrms $\sim$ 30 s that happens from 28,400~K to 28,600~K is due to a discontinuous change in the period spectrum of the models.
-Namely, the appearance of a new mode between the 710 and 784~s modes of the 28,400~K model.
+smooth way, while for others, they exhibit jumps. For instance, the spike 
+in the effective temperature plot at 27,800~K is due to a period (around 530~s) 
+that goes away and then comes back. The model with the missing period fits poorly 
+compared to the models on either side of it. The jump from \sigrms $\sim$ 5 s 
+to \sigrms $\sim$ 30 s that happens from 28,400~K to 28,600~K is due to a discontinuous 
+change in the period spectrum of the models. Namely, the appearance of a new mode 
+between the 710 and 784~s modes of the 28,400~K model.
 
@@
 Dependence of the fitness parameter on different parameters. The 5 parameters other than the one shown 
-on each plot are held to fixed values corresponding to the initial best fit model (table \ref{ffit1}).
-The vertical dashed lines mark the ranges considered in the refined fitting.
-For the envelope mass, we went from \menv = -2.0 to -2.3.
+on the horizontal axis in each plot are held to fixed values corresponding to the initial best fit
+model (table \ref{ffit1}). The vertical dashed lines mark the ranges considered in the refined 
+fitting. For the envelope mass, we went from \menv = -2.0 to -2.3.
  \label{ffit3}
@@
 
-The parameters for our best fit model based on the refined grid are listed in Table \ref{fitt1} and the periods of that model in 
-Table \ref{gd}. The goodness of fit of the model is \sigrms$=0.964$~s. We also list
-the Bayes Information Criterion (BIC) number, a statistic that
+The parameters for our best fit model based on the refined grid are listed in Table \ref{fitt1} 
+and the periods of that model in Table \ref{gd}. The goodness of fit of the model is \sigrms$=0.964$~s. 
+We also list the Bayes Information Criterion (BIC) number, a statistic that
 normalizes the quality of fits by number of free parameters and
 number of constraints for comparison with other studies. For a discussion applied to this parameter
-study, see \citet{Bischoff-Kim11a}.
-A negative BIC indicates a good quality of fit, given the number of constraints.
-One should keepp in mind that the quality of fit is aided by the fact that some of the observed periods have large uncertainties.
+study, see \citet{Bischoff-Kim11a}. A negative BIC indicates a good quality of fit, given the number 
+of constraints. One should keep in mind that the quality of fit is aided by the fact that some of 
+the observed periods have large uncertainties.
 
-In Fig.
-\ref{ffit4} we focus on the mass dependence of the fitness parameter to illustrate the effect a finer grid has on the fitting.
-We could have used less of a fine mesh in mass, but with our very fine mesh, we do get a better view of how the discontinuities first shown in Fig.
-\ref{ffit3} behave and that they are not true discontinuities, just large changes in goodness of fit for small changes in mass.
+In Fig. \ref{ffit4} we focus on the mass dependence of the fitness parameter to illustrate 
+the effect a finer grid has on the fitting. We could have used less of a fine mesh in mass, 
+but with our very fine mesh, we do get a better view of how the discontinuities first shown 
+in Fig. \ref{ffit3} behave and that they are not true discontinuities, just large changes in 
+goodness of fit for small changes in mass.
 
@@
 were very close to the best fit model. We used the period list for a model with parameters 
-${\rm T_{eff}}=25630$~K, $M_*/M_\odot=0.57065$, \menv $=-2.05$ $M_{\rm He}=-5.55$, $X_o=0.52$, and $q_{\rm fm}=0.192$, including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
+${\rm T_{eff}}=25630$~K, $M_*/M_\odot=0.57065$, \menv $=-2.05$ $M_{\rm He}=-5.55$, $X_o=0.52$, and $q_{\rm fm}=0.192$, 
+including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.
 
@@
 the all top 5 best fit models having parameters 
-${\rm T_{eff}}=25000$~K, \menv $=-2.1$, \mhe $=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a mass ranging between  0.5730 and 0.5734 \msun.
-The best fit model has \sigrms $=0.31$~s.
-We remind the reader that
-the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun ~ for stellar mass, 0.1 dex for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
+${\rm T_{eff}}=25000$~K, \mhe $=-2.1$, $M_{\rm env}=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a 
+mass ranging between  0.5730 and 0.5734 \msun. The best fit model has \sigrms $=0.31$~s. We remind t
+he reader that the step sizes in the second phase of the fitting are 50~K for 
+${\rm T_{eff}}$, 0.0001 \msun ~ for stellar mass, 0.1 dex for helium layer masses, 
+0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.
 
-This test also allows us to place minimum error bars on at least some of the parameters found: $\pm 600$ ~ K in effective temperature, 0.05 and 0.02 dex on \menv and \mhe respectively, 0.02 on $X_o$, and 0.002 on $q_{\rm fm}$.
+This test also allows us to place minimum error bars on at least some of the parameters found: $\pm 600$ ~ K in effective 
+temperature, 0.05 and 0.02 dex on \menv and \mhe respectively, 0.02 on $X_o$, and 0.002 on $q_{\rm fm}$.
 
@@
 
-We analyzed archival data and over a thousand hours of new observations on GD358, together covering a span of 33 years.
-With data spanning such a long period of time, we learn about the stability of the different modes.
-We find that the shorter period modes tend to be more stable, while the longer period modes tend to vary more in frequency over time.
-\citet{Bell15} have observed and modeled such stochastic behavior in KIC 4552982, a red edge DAV observed nearly continuously for 1.5 years by \emph{Kepler}.
-In that star, the 361.58 s triplet has sharply defined peaks, while the rest of the modes, with much higher overtone numbers, are less stable.
-The stability of the low k modes is likely due to the fact that they are strongly trapped in the core.
-Unlike their higer k counterparts, they are affected very little by the convection zone near the surface.
+We analyzed archival data and over a thousand hours of new observations on GD358, together covering a 
+span of 33 years. With data spanning such a long period of time, we learn about the stability of the
+different modes. We find that the shorter period modes tend to be more stable, while the longer period 
+modes tend to vary more in frequency over time. \citet{Bell15} have observed and modeled such stochastic 
+behavior in KIC 4552982, a red edge DAV observed nearly continuously for 1.5 years by \emph{Kepler}. 
+In that star, the 361.58 s triplet has sharply defined peaks, while the rest of the modes, with much 
+higher overtone numbers, are less stable. The stability of the low k modes is likely due to the fact 
+that they are strongly trapped in the core. Unlike their higher k counterparts, they are affected very 
+little by the convection zone near the surface.
 
-In analyzing the data, we found 4 new modes, adding to the 11 modes known previously.
-With these 15 modes, we performed a new asteroseismic fit of GD358 with models that include carbon and oxygen core composition profiles based on the stellar evolution models of \citet{Salaris97}.
-We find a best fit effective temperature of 23,650~K and a mass of 0.5706 \msun ~ for GD358.
-While the temperature is close to the recent spectroscopic determination of 24000~K \citep{Koester2013}, the mass is over one sigma above the spectroscopic mass.
-On the other hand, the mass matches almost exactly that found by \citet{Bergeron2011} (but the effective temperature is low).
-The spectroscopic data point of \citet{Koester2013} is somewhat off the asymptotic period spacing trend (Fig.
-\ref{ffit2}, right panel).
+In analyzing the data, we found 4 new modes, adding to the 11 modes known previously. With these 15 modes, 
+we performed a new asteroseismic fit of GD358 with models that include carbon and oxygen core composition 
+profiles based on the stellar evolution models of \citet{Salaris97}. We find a best fit effective temperature 
+of 23,650~K and a mass of 0.5706 \msun ~ for GD358. While the temperature is close to the recent spectroscopic 
+determination of 24000~K \citep{Koester2013}, the mass is over one sigma above the spectroscopic mass. On the 
+other hand, the mass matches almost exactly that found by \citet{Bergeron2011} (but the effective 
+temperature is low). The spectroscopic data point of \citet{Koester2013} is somewhat off the asymptotic 
+period spacing trend (Fig. \ref{ffit2}, right panel).
 
-In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14,Giammichele17}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}.
-We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models.
-We find that cooler best fit models have thicker pure helium envelopes (Fig.
-\ref{ffit5}), in accordance with the outward diffusion of helium over time.
-To be consistent, we used the effective temperature found through the asteroseismic fitting of each star.
-
-%There is one caveat to drawing conclusions from Fig.
-\ref{ffit5}.
-The initial amount of helium in the envelope depends on the mass of the progenitor star and its evolution, with more massive progenitors producing more massive white dwarfs according to the initial-final mass relation.
-Therefore, in order to isolate the effect of diffusion on the mass of the pure helium layer, one would have to consider a single white dwarf mass.
-However, the white dwarf mass distribution is known to be tight, with a range of progenitor masses yielding a narrow range of white dwarf masses.
-We do not believe that our precision in the asteroseismic analyses are at the level where we can use the relationship depicted in Fig.
-\ref{ffit5} to draw quantitative conclusions where the effect of white dwarf mass would matter.
-%
-%Stellar mass also comes into play in diffusion.
-Ideally, we would like all 4 models to have the same mass.
-The models range in mass from 0.525 (EC20058) to 0.640 \msun ~ (CBS114).
-More detailed stellar evolution calculations would have to be performed in order to assess the significance of the trend observed with these 4 DBVs.
+In this study, we varied the parameters that have traditionally been varied in this type of 
+asteroseismic fitting, so that we can place our results side by side with other studies of 
+DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC20058 \citep{Bischoff-Kim11a}, and 
+CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of asteroseismic fitting 
+that used a consistent set of models. We find that cooler best fit models have thicker pure 
+helium envelopes (Fig. \ref{ffit5}), in accordance with the outward diffusion of helium over time. 
+To be consistent, we used the effective temperature found through the asteroseismic fitting of each 
+star. Stellar mass also comes into play in diffusion. Ideally, we would like all 4 models to have 
+the same mass. The models range in mass from 0.525 (EC20058) to 0.640 \msun ~ (CBS114). More detailed 
+stellar evolution calculations would have to be performed in order to assess the significance of the 
+trend observed with these 4 DBVs.
 
@@
 \caption{
-Relationship between effective temperature and pure helium layer mass in 4 DBVs fitted using similar models as GD358 in the present study. \label{ffit5}
+Relationship between effective temperature and pure helium layer mass in 4 DBVs fitted using similar 
+models as GD358 in the present study. \label{ffit5}
 }
@@
 Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with 
-the theory of non-radial oscillations, the shapes of the transition zones matter as much as where they occur \citep{Bischoff-Kim15}.
-Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}.
-We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs.
-It is unclear how much of an effect on structure parameters a change in parameterization would have.
+the theory of non-radial oscillations, the shapes of the transition zones matter as much as where 
+they occur \citep{Bischoff-Kim15}. Modern asteroseismic fitting vary parameters attached to the shape of 
+transition zones \citep{Giammichele15}. We refrained from doing this in the present study because we wanted to 
+compare our results with previous studies of DBVs. It is unclear how much of an effect on structure parameters a 
+change in parameterization would have.
 
-In fitting GD358, we discovered that two very close sets of parameters were able to yield very different fitness parameters.
-This is due to the fact that some periods can change values drastically for a small change in a given parameter.
-The periods tend to oscillate between two values and there remains a well defined minimum in parameter space, even if it is a double valued minimum.
-Any search algorithm that uses a small enough mesh should be able to find the minimum.
-This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
+In fitting GD358, we discovered that two very close sets of parameters were able to yield very different fitness 
+parameters. This is due to the fact that some periods can change values drastically for a small change in a given 
+parameter. The periods tend to oscillate between two values and there remains a well defined minimum in parameter space, 
+even if it is a double valued minimum. Any search algorithm that uses a small enough mesh should be able to find the 
+minimum. This phenomenon likely became apparent while fitting GD358 because it is the first white dwarf for which 
+we fit a long consecutive sequence of modes of the same $\ell$ with high resolution grids.
 
@@
 \enddata
+\tablecomments{Data from the Warwick 1.0m telescope was obtained during an engineering run.}
 \end{deluxetable}

### 2016-08-15 tmp1/msnew.tex
uploading

--- 2016-08-15 msnew.tex
@@
 \begin{abstract}
-We report on the analysis of 34 years of photometric observations of the pulsating
+We report on the analysis of 33 years of photometric observations of the pulsating
 helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
-and 1195.2 hours of new observations from 2007-2016. From this data set, we extract 15 frequencies 
+and 1105.1 hours of new observations from 2007-2015. From this data set, we extract 15 frequencies 
 representing g-mode pulsation modes, adding 4 modes to the 11 modes 
@@
 Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
-New observations presented here include 278 individual observing runs (1105.1 hrs) spanning 
-2007-2016 (Table \ref{journal}). Each season of observations was obtained as part of 
+New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
+2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
 multi-site WET campaigns \citep{wet90}.
@@
 \plotone{noise}
-\caption{A comparison of the average noise as a function of frequency for the 2007-2016 observing 
+\caption{A comparison of the average noise as a function of frequency for the 2007-2015 observing 
 seasons.  Each data set was prewhitened by its dominant frequencies.  The noise levels for each 
@@
 Although the observational timebases and coverage are quite different (20 continuous months 
-for KIC4552982 vs 34 incomplete years for GD358), our data presents the opportunity to investigate this 
+for KIC4552982 vs 33 incomplete years for GD358), our data presents the opportunity to investigate this 
 for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
@@
 
-\citet{Mont2016} recently outlined a possible explanation for the behavior seen in the low frequency modes
-of these cool DAVs that should also apply to GD358. White dwarfs pulsate in nonradial g-modes. As a DBV such as 
-GD358 pulsates, it experiences local surface temperature variations as large as 3000 K.  The temperature 
-variation affects different modes in different ways.  An appropriate analogy is to consider each mode's 
-propagation region as a box with a lid. The box is defined as the region where the mode frequency is 
-less than both the buoyancy (Brunt-V{\"a}is{\"a}l{\"a}) and acoustic (Lamb) frequencies.  The box's lid 
-represents the mode's outer turning point. For short period modes (such as $k=8$ and $k=9$ in GD358), the 
-lid is defined by the acoustic frequency, which is relatively insensitive to surface temperature variations. 
-As the star pulsates, the box will not change, so these modes should be stable.  For the longer period modes, 
-the lid of the box is defined by the buoyancy frequency, which goes to zero at the base of the surface 
-convection zone. This is the important point: for longer period modes, the box lid
-is actually defined by the base of the convection zone, which is very sensitive to local temperature variations.  
-As GD358 pulsates, its convection zone deepens and thins in response to the local temperature variations. 
-In our analogy, the lid of the box moves, effectively changing the characteristics of the box. Long period modes with 
-outer turning points defined by the base of the convection zone should be perturbed and this is indeed 
-what we see in GD358.
-
-An additional interesting behavior is given by the distribution of average amplitudes for the bands 
+A second interesting behavior is given by the distribution of average amplitudes for the bands 
 (Fig~\ref{schematic}). In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
@@
 
-To summarize this section in broad brush strokes, the observed global pulsations involve the whole star, 
-but each pulsation samples the star in slightly different ways.  Modes with lower frequencies 
-(higher radial $k$ values) preferentially sample the outer layers, while modes with higher frequencies 
-(lower radial $k$ values) have outer turning points that are farther from the surface, and so sample the 
-deeper interior. It makes intuitive sense that lower frequency modes would be affected by processes 
-confined to the outer stellar atmosphere, such as the convection zone. We speculate that the 
+In broad brush strokes, the observed global pulsations involve the whole star, but each pulsation samples the star
+in slightly different ways.  For example, modes with lower frequencies (higher radial $k$ values) preferentially 
+sample the outer layers, while modes with higher frequencies (lower radial $k$ values) have outer turning points 
+that are farther from the surface, and so sample the deeper interior. It makes intuitive sense that lower 
+frequency modes would be affected by processes confined to the outer stellar atmosphere. We speculate that the 
 observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface

### 2016-08-15 tmp1/githubcommands.sh

@@ -1,0 +1,17 @@
+#/bin/bash
+
+#series of commands to push changes made locally to server
+git add --all
+git commit
+git push origin master
+
+#series of commands to download changes made on server
+#git fetch upstream
+#git checkout master
+#git merge upstream/master
+
+#list updates about local directory
+#git branch -v
+
+#list remote directories attached to local directory
+#git remote -v

### 2016-10-01 msnew.tex
added Andy
some changes from ref report

@@
 B. Debski\altaffilmark{14,15},
+A. Baran\altaffilmark{15},
 S. Meingast\altaffilmark{16},
@@
 Data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
-were obtained with different CCD photometers, each with distinct effective bandpasses. 
-We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
+were obtained with CCD photometers at multiple sites, each with distinct effective bandpasses. 
+We reduce the bandpass issues by using CCDs with similar detectors whenever possible and 
 employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
-reduce extinction effects. We corrected each image for bias and thermal noise, and 
+minimize extinction effects. We corrected each image for bias and thermal noise, and 
 normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
-described by \citet{Dalessio10} was performed on each image, utilizing a range of 
+described by \citet{Dalessio10} was performed on each image, covering a range of 
 aperture sizes for the target and comparison stars. For each individual nightly run, we 
@@
 
-We used the WQED pipeline \citep{wqed} to examine each nightly light curve for photometric 
+We used the WQED pipeline \citep{wqed} to examine each light curve for photometric 
 quality, remove outlying points, divide by suitable comparison stars, and correct for 
-differential extinction. Our observational technique is therefore not sensitive to 
-oscillations longer than a few hours. The result is a series of light curves 
+differential extinction. This observational technique is therefore not sensitive to 
+oscillations longer than a few hours. The final product is a series of light curves 
 with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
@@
 (an example is shown in Fig. \ref{tersk}) to produce complete light curves for GD358 for each 
-observing season. We assume GD358 oscillates about a mean light level. This assumption 
-allows us to carefully assess overlapping segments from different telescopes and identify 
-and correct any vertical offsets. As discussed in detail in \citet{Provencal09}, we find 
+observing season. As we do for all white dwarf pulators, we assume GD358 oscillates around 
+a mean light level. This assumption allows us to assess overlapping light curves from multiple 
+telescopes and identify and correct any vertical offsets. As discussed in detail in \citet{Provencal09}, we find 
 no significant differences between the noise levels of amplitude spectra using: 
@@
 Our coverage is not complete, and this incompleteness produces spectral leakage in the 
-amplitude spectra. To quantify this, we sampled single sinusoids using exactly the 
+amplitude spectra. To quantify this, our standard procedure samples single sinusoids using exactly the 
 same times as the original data for each season. The resulting amplitude spectrum, 
@@
 We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
-select statistically significant peaks in each FT. We adopt the criterion that a peak must have 
-an amplitude at least four times greater than the average noise level in the given frequency range 
-\citep{Provencal12}. We define ``noise'' as the frequency-dependent 
-average amplitude after removal of the dominant frequencies. This is a conservative estimate, 
-as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
-the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
+identify statistically significant peaks in each FT. We adopt the criterion that a peak must have 
+an amplitude at least four times that of the average noise level in the given frequency range 
+\citep{Provencal12}. This criterion places a 99.9\% probability that the peak represents a real signal,
+and is not a result of random noise \citep{Scargle82, Provencal12}.  We define ``noise'' as the frequency-dependent 
+average amplitude after prewhitening of the dominant frequencies. This is unquestionably a conservative estimate, 
+as it is impractical to assume that all ``real'' frequencies are removed when determining
+the noise level. This is certainly true for GD358, where amplitude modulation is present, and the peaks above $\approx$ 2500 $\mu$Hz\ 
 are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
 as a function of frequency for the 2007-2016 observing seasons. A similar plot for the 
-archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
-estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
-This routine generates a set of light curves using the original times, the fitted frequencies and 
-amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
-curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
-are consistent with our average noise estimates.
+archival data is presented in Fig. 3 of \citet{Provencal09}. We also calculated Monte Carlo 
+simulations using the routine provided in {\sl Period04}.  This routine generates a set of light curves using 
+the original times, the fitted frequencies and amplitudes, and added Gaussian noise. A least squares fit is 
+performed on each simulated light curve, with the distribution of fit parameters giving the uncertainties. 
+Our Monte Carlo results are consistent with our average noise estimates.
 
@@
 Having established our baseline noise levels, we proceed to frequency selection and identification.
-Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
-fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
+Our standard frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
+fitting a sinusoid with that frequency to the data set, subtracting the fit from the light curve, 
 recomputing the FT, examining the residuals, and repeating the process until no significant power 
-remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
-especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
-discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
-modulation is given in \citet{Provencal09}. Our final identifications of independent frequencies
-detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.
+remains. This technique is known as prewhitening. Prewhitening has inherent dangers, and must be 
+employed with extreme vigilance, especially as we are aware of amplitude and/or frequency 
+modulation in our data set. A detailed discussion of the prewhitening procedure and steps 
+taken to minimize the effects of amplitude modulation is given in \citet{Provencal09}. Our final 
+identifications of independent frequencies detected in each observing season are given in 
+Table \ref{freq1} and Table \ref{freq2}.
 
@@
 structures found by \cite{Winget94}, \cite{Kepler03}, \cite{Montgomery10} and others are not real. In 
-particular, it is clear that the $k=12$ mode can be explained by the oblique rotation model during 2006. However, 
+particular, it is clear that the 1741 \muHz\ ($k=12$) mode can be explained by the oblique rotation model during 2006. However, 
 previous work represents short snapshots of GD358. When examined over timescales of decades, these structures 

### 2016-10-01 msnew.tex
a bit more modification (referee report)

@@
 We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
-identify statistically significant peaks in each FT. We adopt the criterion that a peak must have 
+identify statistically significant frequencies in each FT. We adopt the criterion that a peak must have 
 an amplitude at least four times that of the average noise level in the given frequency range 
@@
 average amplitude after prewhitening of the dominant frequencies. This is unquestionably a conservative estimate, 
-as it is impractical to assume that all ``real'' frequencies are removed when determining
-the noise level. This is certainly true for GD358, where amplitude modulation is present, and the peaks above $\approx$ 2500 $\mu$Hz\ 
+as it is impractical to assume that the complete set of ``real'' frequencies are removed when determining
+the noise level. This is inarguably true for GD358, where amplitude modulation is present, and the peaks above $\approx$ 2500 $\mu$Hz\ 
 are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
@@
 Having established our baseline noise levels, we proceed to frequency selection and identification.
-Our standard frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
-fitting a sinusoid with that frequency to the data set, subtracting the fit from the light curve, 
-recomputing the FT, examining the residuals, and repeating the process until no significant power 
+Our standard frequency selection procedure identifies the largest amplitude resolved peak in the FT,
+fits a sinusoid with that frequency to the data set, subtracts the fit from the light curve, 
+recomputes the FT, examines the residuals, and repeates the process until no significant power 
 remains. This technique is known as prewhitening. Prewhitening has inherent dangers, and must be 

### 2016-10-03 msnew.tex
minor change to section 4.1 re: ref report

@@
 do not regularly recur, and so cannot be interpreted as simple rotational splitting. The lower frequency band widths 
-are most likely the result of various processes producing amplitude and/or frequency modulation that obscures any 
-underlying signatures of rotational splitting. 
+are most likely the result of unknown processes that obscure any 
+underlying signatures of simple rotational splitting. 
 \begin{figure}

### 2016-10-04 msnew.tex
changes to Figure 5

@@
 % \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
- \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
- and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1300 \muHz\ band 
- shows no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
+ \caption{The detailed schematic distribution of frequencies for the bands near 1230 ({\em{right}}), 
+1300({\em{middle}}), and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1230 and 
+1300 \muHz\ bands  show no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
  structure. Assuming the triplet represents

### 2016-10-05 msnew.tex
more changes ref report

@@
 known previously. We present evidence that these 15 modes are $\ell=1$ modes, 13 of which belong to 
-a consecutive sequence in radial overtone
-$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
-core composition profiles to fit the periods.
-Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex.
-The surface gravity translates to a mass range of 0.455 to 0.540 \msun.
-Our best fit model has a temperature of 23,650~K and a mass of 0.5706 \msun ~.
-That is slightly more massive than what the most recent spectroscopy suggests.
-We find a pure helium layer mass of $10^{-5.50}$, consistent with the outward diffusion of helium over time.
+a consecutive sequence in radial overtone $k$. We perform a detailed asteroseismic analysis using 
+models that include parameterized, complex carbon and oxygen core composition profiles to fit the periods. 
+Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 
+24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex. The surface gravity translates to a mass range 
+of 0.455 to 0.540 \msun. Our best fit model has a temperature of 23,650~K and a mass of 
+0.5706 \msun ~. That is slightly more massive than what the most recent spectroscopy suggests. We 
+find a pure helium layer mass of $10^{-5.50}$, consistent with the outward diffusion of helium over time.
 
@@
 dwarfs, with most of the remaining 80\% consisting of their hydrogen atmosphere (DA) 
-cousins. One theory behind the bifurcation into two spectral classes is that during post-AGB evolution, a very late thermal pulse can burn off the residual hydrogen 
+cousins. One theory behind the bifurcation into two spectral classes is that during post-AGB evolution, 
+a very late thermal pulse can burn off the residual hydrogen 
 in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
@@
 \citep{Nitta12, Koester2013}. GD358's pulsation spectrum contains a series of independent 
-radial overtones, many with complex frequency structure.
-For one epoch of data taken during a WET run, models involving magnetic fields and oblique rotation have been proposed to explain such structure \citep{Montgomery10}.
+radial overtones, many with complex frequency structure.  For one epoch of data taken during a WET run, 
+models involving magnetic fields and oblique rotation have been proposed to explain such structure \citep{Montgomery10}.
 
@@
 The present analysis also allows us to place GD358 in the context of stellar evolution. 
-According to the models, the precursors of DBs emerge from the born-again phase with 
-envelopes containing a nearly uniform mixture of helium (He), carbon (C), and oxygen (O) 
-out to the photosphere \citep{Dreizler98,Herwig99}. As the PG 1159 stars cool, the helium 
-diffuses upward and gradually accumulates to form a chemically pure surface layer. Through 
-the DBV instability strip, this process is still ongoing so that instead of a pure helium 
-layer surrounding the carbon and oxygen core, one has a region where the carbon and helium 
-are still mixed. This leads to a double layered structure, with the pure He surface layer 
-overlying the remainder of the uniform He/C/O envelope, all above the degenerate C/O core. 
-A key prediction of the diffusion models is that, for a given stellar mass, the pure He 
-surface layer will steadily grow thicker as the DB star cools.  GD358 is the fourth DBV 
-we can use to check this theory. The other three DBVs 
+According to the models, DB progenitors emerge from the born-again phase with 
+envelopes composed of a nearly uniform mixture of helium (He), carbon (C), and oxygen (O) 
+out to the photosphere \citep{Dreizler98,Herwig99}. As these stars cool, the mixed helium 
+diffuses upward and begins to form a chemically pure helium surface layer. The resulting
+expected structure is double layered, with a pure He surface layer overlying a uniformly 
+mixed He/C/O envelope, all above the degenerate C/O core. A key prediction of diffusion models 
+is that, for a given stellar mass, the surface He surface layer will grow thicker as the DB 
+cools. The DBVs provide an important test of this prediction: we should find an increase in 
+helium layer thickness for DBVs across the helium instability strip.  DBV GD358 is the fourth 
+DBV we can use to check this theory. The other three DBVs 
 (\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture qualitatively consistent with 
@@
 Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
-New observations presented here include 278 individual observing runs (1105.1 hrs) spanning 
+New observations presented here include 278 individual observing runs (1195.1 hrs) spanning 
 2007-2016 (Table \ref{journal}). Each season of observations was obtained as part of 
@@
 Data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
-were obtained with CCD photometers at multiple sites, each with distinct effective bandpasses. 
-We reduce the bandpass issues by using CCDs with similar detectors whenever possible and 
+were obtained with CCD photometers placed at multiple sites.  Each photometer has its own 
+distinct effective bandpasses, which could influence the observed pulsation amplitudes. We strive 
+to reduce these bandpass issues by using CCD photometers with similar detectors whenever possible and 
 employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
 minimize extinction effects. We corrected each image for bias and thermal noise, and 
-normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
-described by \citet{Dalessio10} was performed on each image, covering a range of 
+normalized by the flat field. We performed aperture photometry on each image 
+using the Maestro photometry pipeline described by \citet{Dalessio10}. Maestro automatically covers a range of 
 aperture sizes for the target and comparison stars. For each individual nightly run, we 
@@
 quality, remove outlying points, divide by suitable comparison stars, and correct for 
-differential extinction. This observational technique is therefore not sensitive to 
-oscillations longer than a few hours. The final product is a series of light curves 
-with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
-representation of the fractional intensity of modulation (1 mmi $\approx$ 1 mmag). We present
+differential extinction. Since we rely on relative photometry by dividing by comparison stars,
+our observational technique is not sensitive to oscillations with periods longer than a few hours. 
+The final product is a series of light curves with amplitude variations represented as fractional intensity (mmi). 
+The unit is a linear representation of the fractional intensity of modulation (1 mmi $\approx$ 1 mmag). We present
 our Fourier transforms (FTs) in units of modulation amplitude 
@@
 
-The final reduction step is to combine the individual light curves 
-(an example is shown in Fig. \ref{tersk}) to produce complete light curves for GD358 for each 
+Our final reduction step is to combine the individual light curves 
+(an example is shown in Fig. \ref{tersk}) to create complete light curves for GD358 for each 
 observing season. As we do for all white dwarf pulators, we assume GD358 oscillates around 
@@
 no significant differences between the noise levels of amplitude spectra using: 
-1) the combination of all light curves including overlapping 
+1) the combination of every light curve including overlapping 
 segments from different telescopes, 2) the combination of light curves where we retain 
-only higher signal to noise observations in overlapping segments and 3) combining all light 
-curves using data weighted by telescope aperture.
+the high signal to noise observations in overlapping segments and 3) combining all light 
+curves incorporating data weighted by telescope aperture.
 
@@
 2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, 2015 55 hrs and 2016 90.6 hrs. 
-Our coverage is not complete, and this incompleteness produces spectral leakage in the 
-amplitude spectra. To quantify this, our standard procedure samples single sinusoids using exactly the 
-same times as the original data for each season. The resulting amplitude spectrum, 
+We are limited to ground based facilites with inherent weather issues, so our coverage is not continuous. This 
+incompleteness produces spectral leakage in the amplitude spectra. To quantify this, our standard procedure 
+samples single sinusoids using the exact times as the original data for each season. The resulting amplitude spectrum, 
 or ``spectral window'', is the pattern produced in the FT by a single frequency. 
@@
 \begin{figure}
-\plotone{gd358multidft}
+\plotone{gd358multidft.jpg}
 \caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
@@
 We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
-identify statistically significant frequencies in each FT. We adopt the criterion that a peak must have 
-an amplitude at least four times that of the average noise level in the given frequency range 
+identify statistically significant frequencies in each observing season. Our standard procedure is to adopt the criterion 
+that any peak have an amplitude at least four times above the average noise level in the given frequency range 
 \citep{Provencal12}. This criterion places a 99.9\% probability that the peak represents a real signal,
 and is not a result of random noise \citep{Scargle82, Provencal12}.  We define ``noise'' as the frequency-dependent 
-average amplitude after prewhitening of the dominant frequencies. This is unquestionably a conservative estimate, 
+average amplitude after removal of the dominant frequencies. This is unquestionably a conservative estimate, 
 as it is impractical to assume that the complete set of ``real'' frequencies are removed when determining
@@
 archival data is presented in Fig. 3 of \citet{Provencal09}. We also calculated Monte Carlo 
-simulations using the routine provided in {\sl Period04}.  This routine generates a set of light curves using 
+simulations using the routine provided in {\sl Period04}.  This routine generates a data set using 
 the original times, the fitted frequencies and amplitudes, and added Gaussian noise. A least squares fit is 
@@
 fits a sinusoid with that frequency to the data set, subtracts the fit from the light curve, 
-recomputes the FT, examines the residuals, and repeates the process until no significant power 
+recomputes the FT, examines the residuals, and repeats the process until no significant power 
 remains. This technique is known as prewhitening. Prewhitening has inherent dangers, and must be 
@@
 
-Fig.~\ref{schematic} presents a schematic representation of GD358's 
-independent frequencies detected between 1982 and 2016.  
+Fig.~\ref{schematic} presents a schematic representation of all GD358's independent frequencies 
+detected between 1982 and 2016. The figure contains all peaks that meet our detection criteria, and so
+represents the natural distribution of GD358's pulsation frequencies.  
 The features of asteroseismic importance are the localized bands between 900 and 2400
@@
 previous work represents short snapshots of GD358. When examined over timescales of decades, these structures 
-do not regularly recur, and so cannot be interpreted as simple rotational splitting. The lower frequency band widths 
+do not regularly recur, and so cannot be interpreted as simple rotational splitting. The widths of the lower frequency bands
 are most likely the result of unknown processes that obscure any 
@@
 
-\citet{Mont2016} recently outlined a possible explanation for the behavior seen in the low frequency modes
+\citet{Mont2016} recently presented a possible explanation for the behavior seen in the low frequency modes
 of these cool DAVs that should also apply to GD358. White dwarfs pulsate in nonradial g-modes. As a DBV such as 
@@
 
-Finally, given the $l$=1 identification and the lack of definitive multiplet structure for the lower 
-frequency modes, the best way to determine the central frequency for each band is simply to 
-average the detected frequencies in the bands.  We experimented with numerous weighting techniques, 
-and determined there is no significant difference in our solutions.  Our final frequencies for each band 
-are given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.
+Finally, since the asteroseismic fitting deals with periods, we need to determine a period for each band 
+to be used in the asteroseismic fits. Given the $l$=1 identification and the lack of definitive multiplet 
+structure for the lower frequency modes, the best way to determine the central period for each band is simply 
+to average the detected frequencies in each band. One might question why we do not use the central components 
+of the triplets for the shorter period ($k$=9 and 8) bands. The triplets do not have exactly equal splittings, 
+and the central components wander in frequency over time \citep{Provencal09}. It is probable that some process, 
+such as magnetic fields, is offsetting the central components. We therefore decided to treat 
+all the bands with the same protocol. We experimented with numerous weighting techniques, and determined 
+there is no significant difference in our solutions.  Our measured periods for each band 
+are given in Table~\ref{gd}. The errors given are the uncertainties in the mean. We use these periods in 
+our asteroseismic fitting.
 
